---
title: "Exercises 5: Data wrangling I"
author: "Introduction to data science: session 8"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(scales)
library(gradethis)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```

## Content quiz

```{r wrangquiz}
quiz(
  question(
    "What is 'tidy data'?", 
    answer(paste0(
      "A description of a way to organize data that allows for ",
      "easy further processing of this data for the sake of ",
      "analysis or visualization"), 
      correct = TRUE),
    answer("Data that was collected in a convincing way"),
    answer("Data that is publicly available and that can be directly processed further"),
    answer("Data that is documented in a way that others can use it"),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is the main goal of wrangling data that we discussed so far?", 
    answer("To transform raw data into tidy data", correct = TRUE),
    answer("To coerce data into `tibble`s"),
    answer("To import data into R without chaning it"),
    answer("To identify the right way to model the data"),
    answer("To manipulate data in a transparent and reproducible way"),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    paste0(
    "Which of the following demands is part of the definition of tidy data?"
    ),
    answer('Every row corresponds to one and only one observation', correct = TRUE),
    answer('Every column corresponds to one and only one variable', correct = TRUE),
    answer('Every cell corresponds to one and only one value', correct = TRUE),
    answer('The data is stored in a `tibble`'),
    answer('There are no illegal variable names'),
    answer('Data were collected in a transparent and convincing way'),
    answer('Data are stored in a subdirectory `data`'),
    allow_retry = TRUE, random_answer_order = TRUE
  ), 
  question(
    "How is 'long' data different from 'wide' data?", 
    answer("Long data has relative more rows, but fewer columns", correct = TRUE),
    answer("Long data has relative more columns, but fewer rows"),
    answer("The data set are bigger in size"),
    answer("They are easier to read by humans"),
    answer("Wide data can be used as input for modeling and visualization functions"),
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

Consider the following code:

```{r, eval=FALSE, echo=TRUE}
final_data <- filter(base_data, gender=="male")
final_data <- select(final_data, all_of(c("height", "weight")))
final_data <- mutate(final_data, weight_per_cm=weight/height)
```

```{r wquiz2}
quiz(
  question("How could you re-write it using pipes?",
    answer("`final_data <- base_data %>%
    filter(gender=='male') %>% 
    select(all_of(c('height', 'weight'))) %>%
    mutate(final_data, weight_per_cm=weight/height)`", 
    correct = TRUE),
    answer("`final_data <- base_data %>%
    filter(base_data, gender=='male') %>% 
    select(base_data, all_of(c('height', 'weight'))) %>%
    mutate(base_data, final_data, weight_per_cm=weight/height)`"),
    answer("`final_data <- base_data %>%
    filter(..., gender=='male') %>% 
    select(..., all_of(c('height', 'weight'))) %>%
    mutate(..., final_data, weight_per_cm=weight/height)`"),
    answer("This is not possible"),
    answer("`final_data <- base_data ->
    filter(gender=='male') -> 
    select(all_of(c('height', 'weight'))) ->
    mutate(final_data, weight_per_cm=weight/height)`"),
    allow_retry = TRUE, random_answer_order = TRUE
)
)
```

## Coding exercises - Part 1

In the following exercises, please make sure that you return your final data
set, otherwise your solution cannot be evaluated. This means the the following
does not work:

```{r, eval=FALSE, echo=TRUE}
my_solution <- data.frame("a"=1:2, "b"=3:4)
```

Instead, write:

```{r, eval=FALSE, echo=TRUE}
my_solution <- data.frame("a"=1:2, "b"=3:4)
my_solution
```

Or:

```{r, eval=FALSE, echo=TRUE}
data.frame("a"=1:2, "b"=3:4)
```

### Creating new columns

```{r ex-wrang3-setup}
set.seed(123)
frame_1 <- tibble(
  height=rnorm(5, mean = 10),
  width=rnorm(5, mean = 10)
)
```

Consider the data set `frame_1`:

```{r}
set.seed(123)
frame_1 <- tibble(
  height=rnorm(5, mean = 10),
  width=rnorm(5, mean = 10)
)
frame_1
```

Create a new column called `area` that contains the product of the two columns
`height` and `width`!

```{r ex-wrang3, exercise=TRUE}

```

```{r ex-wrang3-hint-1}
frame_1 %>%
  dplyr::____(____=____)
```

```{r ex-wrang3-hint-2}
frame_1 %>%
  dplyr::mutate(____=____)
```

```{r ex-wrang3-hint-3}
frame_1 %>%
  dplyr::mutate(area=____)
```

```{r ex-wrang3-hint-4}
frame_1 %>%
  dplyr::mutate(area=____*____)
```

```{r ex-wrang3-hint-5}
frame_1 %>%
  dplyr::mutate(area=height*____)
```

```{r ex-wrang3-solution}
frame_1 %>%
  dplyr::mutate(area=height*width)
```

```{r ex-wrang3-check}
frame_1_sol <- frame_1 %>%
  dplyr::mutate(area=height*width)

grade_this({
  fail_if(!"area" %in% names(.result), 
          message = paste0("Your result should contain a column `area`!"))
  pass_if(identical(.result, frame_1_sol))
  fail()
})
```


### Filtering rows

```{r ex-wrang4-setup}
set.seed(123)
height_obs <- tibble(
  height=round(rnorm(5, mean = 175, sd = 15))
)
```

Consider the data set `height_obs`:

```{r}
set.seed(123)
height_obs <- tibble(
  height=round(rnorm(5, mean = 175, sd = 15))
)
height_obs
```

Filter the data such that it only contains rows where the height is 
greater of equal to `176`!

```{r ex-wrang4, exercise=TRUE}

```

```{r ex-wrang4-hint-1}
height_obs %>%
  dplyr::____(____)
```

```{r ex-wrang4-hint-2}
height_obs %>%
  dplyr::filter(____)
# Maybe have a look at the filter help page?
```

```{r ex-wrang4-hint-3}
height_obs %>%
  dplyr::filter(height____)
```

```{r ex-wrang4-hint-4}
height_obs %>%
  dplyr::filter(height>=____)
```

```{r ex-wrang4-solution}
height_obs %>%
  dplyr::filter(height>=176)
```

```{r ex-wrang4-check}
height_obs_sol <- height_obs %>%
  dplyr::filter(height>=176)

grade_this({
  fail_if(min(.result$height!=min(height_obs_sol$height)), 
          message = paste0(
            "You should filter for a height of greater or equal to 176! ", 
            "The smallest value in your result is {round(min(.result), 2)}, ",
            "so there must be something wrong with the logical operators you ",
            "have used!")
          )
  pass_if(identical(.result, height_obs_sol))
  fail()
})
```

### Selecting columns

```{r ex-wrang5-setup}
develop_data <- DataScienceExercises::aggGDPlifexp %>%
  dplyr::filter(year>=1997, continent=="Africa")
```

Consider the data set `develop_data` from above. Select the columns 
`continent`, `year`, and `lifeExp`.
While not strictly necessary, please make use of the function `dplyr::all_of()`
in your solution!

```{r ex-wrang5, exercise=TRUE}

```

```{r ex-wrang5-hint-1}
develop_data %>%
  dplyr::____(____)
```

```{r ex-wrang5-hint-2}
develop_data %>%
  dplyr::select(____)
# Maybe have a look at the select help page?
```

```{r ex-wrang5-hint-3}
develop_data %>%
  dplyr::select(dplyr::all_of(____))
```

```{r ex-wrang5-hint-4}
develop_data %>%
  dplyr::select(dplyr::all_of(c(____)))
```

```{r ex-wrang5-hint-5}
develop_data %>%
  dplyr::select(dplyr::all_of(c(____, ____, ____)))
```

```{r ex-wrang5-hint-6}
develop_data %>%
  dplyr::select(dplyr::all_of(c("continent", ____, ____)))
```

```{r ex-wrang5-solution}
develop_data %>%
  dplyr::select(dplyr::all_of(c("continent", "year", "lifeExp")))
```

```{r ex-wrang5-check}
develop_data_selected <- develop_data %>%
  dplyr::select(dplyr::all_of(c("continent", "year", "lifeExp")))

grade_this({
  fail_if(stringr::str_count(.user_code, "all_of")<1, 
          message = paste0(
            "Your solution should include the function `dplyr::all_of()`!", 
            "While it is not strictly necessary you should learn how to use it.",
            "It turns out to be very useful in practice since it accepts ",
            "column names as characters!")
          )
  pass_if(identical(.result, develop_data_selected))
  fail()
})
```

### Wide and long data I

Consider the relatively wide data set `develop_data`:

```{r, echo=FALSE}
develop_data <- DataScienceExercises::aggGDPlifexp %>%
  dplyr::filter(year>=1997, continent=="Africa")
develop_data
```

Make this data set longer such that it gets the following structure:

```{r, echo=FALSE}
develop_data %>%
  pivot_longer(
    cols = all_of(c("year", "lifeExp", "pop", "gdpPercap")), 
    names_to = "variable_considered", 
    values_to = "value_observed") %>%
  head(4)
```

```{r ex-wrang1-setup}
develop_data <- DataScienceExercises::aggGDPlifexp %>%
  dplyr::filter(year>=1997, continent=="Africa")
```

```{r ex-wrang1, exercise=TRUE}

```

```{r ex-wrang1-hint-1}
develop_data %>%
  tidyr::____(
    ____ = ____, 
    ____ = ____, 
    ____ = ____)
```

```{r ex-wrang1-hint-2}
develop_data %>%
  tidyr::pivot_longer(
    ____ = ____, 
    ____ = ____, 
    ____ = ____)
# Maybe have a look at ?pivot_longer
```

```{r ex-wrang1-hint-3}
develop_data %>%
  tidyr::pivot_longer(
    cols = ____, 
    names_to = ____, 
    values_to = ____)
```

```{r ex-wrang1-hint-4}
develop_data %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c(____)), 
    names_to = ____, 
    values_to = ____)
```

```{r ex-wrang1-hint-5}
develop_data %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("year", "lifeExp", "pop", "gdpPercap")), 
    names_to = ____, 
    values_to = ____)
```

```{r ex-wrang1-hint-6}
develop_data %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("year", "lifeExp", "pop", "gdpPercap")), 
    names_to = "variable_considered", 
    values_to = ____)
```

```{r ex-wrang1-solution}
develop_data %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("year", "lifeExp", "pop", "gdpPercap")), 
    names_to = "variable_considered", 
    values_to = "value_observed")
```

```{r ex-wrang1-check}
develop_data_sol <- develop_data %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("year", "lifeExp", "pop", "gdpPercap")), 
    names_to = "variable_considered", 
    values_to = "value_observed")

grade_this({
  fail_if(!"variable_considered" %in% names(.result), 
          message = paste0("Keep in mind that your result should include ",
                           "a column named 'variable_considered'!"))
  fail_if(!"value_observed" %in% names(.result), 
          message = paste0("Keep in mind that your result should include ",
                           "a column named 'value_observed'!"))
  pass_if(identical(.result, develop_data_sol))
  fail()
})
```

### Wide and long data II

Consider the relatively long data set `asian_data`:

```{r, echo=FALSE}
asian_data <- DataScienceExercises::gdplifexp2007 %>%
  dplyr::filter(country %in% c("China", "India", "Indonesia", "Japan")) %>%
  dplyr::select(-continent) %>%
  tidyr::pivot_longer(cols = -country, names_to = "var", values_to = "val")
asian_data
```

Make this data set wider such that it gets the following structure:

```{r, echo=FALSE}
asian_data_wide <- asian_data %>%
  tidyr::pivot_wider(names_from = "country", values_from = "val")
asian_data_wide
```

```{r ex-wrang2-setup}
asian_data <- DataScienceExercises::gdplifexp2007 %>%
  dplyr::filter(country %in% c("China", "India", "Indonesia", "Japan")) %>%
  dplyr::select(-continent) %>%
  tidyr::pivot_longer(cols = -country, names_to = "var", values_to = "val")
```

```{r ex-wrang2, exercise=TRUE}

```

```{r ex-wrang2-hint-1}
asian_data %>%
  tidyr::____(
    ____ = ____, 
    ____ = ____)
```

```{r ex-wrang2-hint-2}
asian_data %>%
  tidyr::pivot_wider(
    ____ = ____, 
    ____ = ____)
# Maybe have a look at ?pivot_wider
```

```{r ex-wrang2-hint-3}
asian_data %>%
  tidyr::pivot_wider(
    names_from = ____, 
    ____ = ____)
```

```{r ex-wrang2-hint-4}
asian_data %>%
  tidyr::pivot_wider(
    names_from = ____, 
    values_from = ____)
```

```{r ex-wrang2-hint-5}
asian_data %>%
  tidyr::pivot_wider(
    names_from = "country", 
    values_from = ____)
```

```{r ex-wrang2-solution}
asian_data_wide <- asian_data %>%
  tidyr::pivot_wider(
    names_from = "country", 
    values_from = "val")
asian_data_wide
```

```{r ex-wrang2-check}
asian_data_wide <- asian_data %>%
  tidyr::pivot_wider(names_from = "country", values_from = "val")

grade_this({
  fail_if(!"China" %in% names(.result), 
          message = paste0("Make sure you choose the right column as source ",
                           "for the new column names!"))
  pass_if(identical(.result, asian_data_wide))
  fail()
})
```

## Coding exercises - Part 2

### Joining data sets I

```{r ex-wrang6-setup}
unemp_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "labor_force") %>%
  dplyr::filter(year>2016) %>%
  dplyr::rename(Country=country, Year=year)

pop_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "population") %>%
  dplyr::filter(year<2019)
```

```{r}
unemp_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "labor_force") %>%
  dplyr::filter(year>2016) %>%
  dplyr::rename(Country=country, Year=year)

pop_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "population") %>%
  dplyr::filter(year<2019)
```

Consider the following two data sets:

```{r, echo=TRUE}
unemp_data
```

and 

```{r, echo=TRUE}
pop_data
```

Join these data sets into one single data set containing 
observations for the population and labor force in Germany for
each year such that this data set only contains those years for which data
on both population and labor force is available (i.e. no missing value occur).

```{r ex-wrang6, exercise=TRUE}

```

```{r ex-wrang6-hint-1}
dplyr::____(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang6-hint-2}
dplyr::____join(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang6-hint-3}
dplyr::inner_join(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang6-hint-4}
dplyr::inner_join(
  x = ____, y = ____, 
  ____=____
  )
```

```{r ex-wrang6-hint-5}
dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  ____=____
  )
```

```{r ex-wrang6-hint-6}
dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  by=____
  )
```

```{r ex-wrang6-hint-7}
dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  by=c(____=____, ____=____)
  )
```

```{r ex-wrang6-hint-8}
dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", ____=____)
  )
```

```{r ex-wrang6-solution}
dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", "Year"="year")
  )
# Note: if you switch unemp_data and pop_data, you also need to swap the 
# names in the by argument
```

```{r ex-wrang6-check}
unemp_pop_data_1 <- dplyr::inner_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", "Year"="year")
  )

unemp_pop_data_2 <- dplyr::inner_join(
  x = pop_data, y = unemp_data, 
  by=c("country"="Country", "year"="Year")
  )

grade_this({
  fail_if(!stringr::str_detect(.user_code, "_join"), 
          message = paste0("There is a family of functions provided in the ",
                           "dplyr package that allow you to join data sets. ",
                           "Use one of them!"))
  fail_if(!stringr::str_detect(.user_code, "inner_join"), 
          message = paste0("You did not choose the right member of the ",
                           "dplyr::join_*-family. Maybe have a look at the ",
                           "documentation?!"))
  pass_if(identical(.result, unemp_pop_data_1) | identical(.result, unemp_pop_data_2))
  fail()
})
```


### Joining data sets II

Use the same data sets as in the previous exercise but now join the data sets
such that all years for which at least one observation in one of the two 
variables is available are contained in the new data set.

```{r ex-wrang7-setup}
unemp_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "labor_force") %>%
  dplyr::filter(year>2016) %>%
  dplyr::rename(Country=country, Year=year)

pop_data <- DataScienceExercises::unemp_pop %>%
  dplyr::select("country", "year", "population") %>%
  dplyr::filter(year<2019)
```

```{r ex-wrang7, exercise=TRUE}

```

```{r ex-wrang7-hint-1}
dplyr::____(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang7-hint-2}
dplyr::____join(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang7-hint-3}
dplyr::full_join(
  ____ = ____, ____ = ____, 
  ____=____
  )
```

```{r ex-wrang7-hint-4}
dplyr::full_join(
  x = ____, y = ____, 
  ____=____
  )
```

```{r ex-wrang7-hint-5}
dplyr::full_join(
  x = unemp_data, y = pop_data, 
  ____=____
  )
```

```{r ex-wrang7-hint-6}
dplyr::full_join(
  x = unemp_data, y = pop_data, 
  by=____
  )
```

```{r ex-wrang7-hint-7}
dplyr::full_join(
  x = unemp_data, y = pop_data, 
  by=c(____=____, ____=____)
  )
```

```{r ex-wrang7-hint-8}
dplyr::full_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", ____=____)
  )
```

```{r ex-wrang7-solution}
dplyr::full_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", "Year"="year")
  )
# Note: if you switch unemp_data and pop_data, you also need to swap the 
# names in the by argument
```

```{r ex-wrang7-check}
unemp_pop_data_1 <- dplyr::full_join(
  x = unemp_data, y = pop_data, 
  by=c("Country"="country", "Year"="year")
  )

unemp_pop_data_2 <- dplyr::full_join(
  x = pop_data, y = unemp_data, 
  by=c("country"="Country", "year"="Year")
  )

grade_this({
  fail_if(!stringr::str_detect(.user_code, "_join"), 
          message = paste0("There is a family of functions provided in the ",
                           "dplyr package that allow you to join data sets. ",
                           "Use one of them!"))
  fail_if(!stringr::str_detect(.user_code, "full_join"), 
          message = paste0("You did not choose the right member of the ",
                           "dplyr::join_*-family. Maybe have a look at the ",
                           "documentation?!"))
  pass_if(identical(.result, unemp_pop_data_1) | identical(.result, unemp_pop_data_2))
  fail()
})
```


### Summarizing data

Consider the data set `wine2dine` , which contains information about the alcohol
and sugar content, as well as the perceived quality of 6497 red and white wines:

```{r}
wine2dine <- DataScienceExercises::wine2dine
head(wine2dine)
```

Compute the averages of the three wine 
properties for white and red wine separately. Your result should be a 
`tibble` that contains a column `property` indicating the property, and the 
columns `red` and `white`, which contain the average values for red and 
white wine, respectively. It should look like this:

```{r}
tibble("property"=rep(NA_character_, 3), 
       "red"=rep(NA_real_, 3), 
       "white"=rep(NA_real_, 3))
```


```{r ex-wrang8-setup}
wine2dine <- DataScienceExercises::wine2dine
```

```{r ex-wrang8, exercise=TRUE}

```

```{r ex-wrang8-hint-1}
wine2dine %>%
  tidyr::____(____) %>%
  dplyr::____(____) %>%
  dplyr::____(____) %>%
  tidyr::____(____)
```

```{r ex-wrang8-hint-2}
wine2dine %>%
  tidyr::pivot_longer(____) %>%
  dplyr::____(____) %>%
  dplyr::____(____) %>%
  tidyr::____(____)
```

```{r ex-wrang8-hint-3}
wine2dine %>%
  tidyr::pivot_longer(____) %>%
  dplyr::group_by(____) %>%
  dplyr::____(____) %>%
  tidyr::____(____)
```

```{r ex-wrang8-hint-4}
wine2dine %>%
  tidyr::pivot_longer(____) %>%
  dplyr::group_by(____) %>%
  dplyr::summarise(____) %>%
  tidyr::____(____)
```

```{r ex-wrang8-hint-5}
wine2dine %>%
  tidyr::pivot_longer(____) %>%
  dplyr::group_by(____) %>%
  dplyr::summarise(____) %>%
  tidyr::pivot_wider(____)
```

```{r ex-wrang8-hint-6}
wine2dine %>%
  tidyr::pivot_longer(    
    cols = dplyr::all_of(____), 
    names_to = ____, 
    values_to = ____) %>%
  dplyr::group_by(____) %>%
  dplyr::summarise(____) %>%
  tidyr::pivot_wider(____)
```

```{r ex-wrang8-hint-7}
wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(____) %>%
  dplyr::summarise(____) %>%
  tidyr::pivot_wider(____)
```

```{r ex-wrang8-hint-8}
wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(kind, property) %>%
  dplyr::summarise(____) %>%
  tidyr::pivot_wider(____)
```

```{r ex-wrang8-hint-9}
wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(kind, property) %>%
  dplyr::summarise(value=mean(value), .groups = "drop") %>%
  tidyr::pivot_wider(____)
```

```{r ex-wrang8-hint-10}
wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(kind, property) %>%
  dplyr::summarise(value=mean(value), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = ____, values_from = ____)
```

```{r ex-wrang8-solution}
wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(kind, property) %>%
  dplyr::summarise(value=mean(value), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "kind", values_from = "value")
```

```{r ex-wrang8-check}
wine2dine_sol <- wine2dine %>%
  tidyr::pivot_longer(
    cols = dplyr::all_of(c("alcohol", "quality", "residual sugar")), 
    names_to = "property", 
    values_to = "value") %>%
  dplyr::group_by(kind, property) %>%
  dplyr::summarise(value=mean(value), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "kind", values_from = "value")

grade_this({
  fail_if(!tibble::is_tibble(.result), 
          message = "Your result should be a `tibble`, not a {typeof(.result)}!")
  
  fail_if(!stringr::str_detect(.user_code, "pivot_longer"), 
          message = paste0("The solution is a bit more complex! It must ",
                           "definitely make use of the function ",
                           "`tidyr::pivot_longer()`. Think of how and where ",
                           "it might help you!"))
  
  fail_if(!stringr::str_detect(.user_code, "group_by"), 
          message = paste0("The solution is a bit more complex! It must ",
                           "definitely make use of the function ",
                           "`dplyr::group_by()`. Think of how and where ",
                           "it might help you!"))
  
  fail_if(!(stringr::str_detect(.user_code, "summarise") | 
              stringr::str_detect(.user_code, "summarize")), 
          message = paste0("The solution is a bit more complex! It must ",
                           "definitely make use of the function ",
                           "`dplyr::summarise()`. Think of how and where ",
                           "it might help you!"))
  
  fail_if(!stringr::str_detect(.user_code, "pivot_wider"), 
          message = paste0("The solution is a bit more complex! It must ",
                           "definitely make use of the function ",
                           "`tidyr::pivot_wider()`. Think of how and where ",
                           "it might help you!"))
  
  fail_if(!setequal(names(.result), names(wine2dine_sol)), 
          message = paste0(
            "There is a problem with the names of your `tibble`. They should ",
            "be `'property'`, `'red'`, and `'white'`, ",
            "not {paste(names(.result), collapse=', ')}!"
            )
          )
  
  pass_if(identical(.result, wine2dine_sol))
  fail()
})
```
