---
title: "Exercises 1: Basics in R"
author: "Introduction to data science: session 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```

## General remarks
*You should complete these exercises at least once before the next lecture.*
*In case you do not understand a solution, please make a post on the course*
*homepage and discuss your problems with the other participants. In case this*
*does not help we can take up the problem in the next session. Please note that*
*feedback on the exercises is highly welcome!*

## Objects, functions, and assignments

### Content quiz

```{r assignquiz}
quiz(
  question(
    "Which of the following commands is equivalend to `xx <- 2`?",
    answer('assign("xx", 2)', correct = TRUE),
    answer("xx -> 2"),
    answer("name('xx', 2)"),
    answer("assign(xx, 2)"), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Which of the following statements about objects and names is correct?",
    answer("Every object can only have a unique name, just as every name must point to a unique object)!"),
    answer("While every object must have a unique name, each name can point to none, one, or several objects!"),
    answer("Names can point to multiple objects, and objects can have more than one name."),
    answer("An object can have many names, only every name must point to a unique object", 
           correct = TRUE), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What can you do to remove all object-name assignment in your current R session?",
    answer("Restart the R session!"),
    answer("Call `rm(name)` for each assignment.", 
           correct = TRUE),
    answer("Click on the broom in the upper right environment panel in R-Studio", 
           correct = TRUE),
    answer("Call `rm(list=ls())` in the console.", 
           correct = TRUE),
    answer("Remove the assignment from the script and re-run the script from above."), 
    allow_retry = TRUE, random_answer_order = TRUE
    )
)
```

### Coding exercise 

Compute the following mathematical operations in R:

$$10+25$$

```{r ex-addition, exercise=TRUE}

```

<div id="ex-addition-hint">
**Hint:** It might be a good idea to search for something like 'addition in R' in the web.
</div>

```{r ex-addition-check}
grade_result(
  pass_if(~identical(.result, 10+25))
)
```

$$50\cdot 2$$

```{r ex-multiplication, exercise=TRUE}

```

<div id="ex-multiplication-hint">
**Hint:** It might be a good idea to search for something like 'multiplication in R' in the web.
</div>

```{r ex-multiplication-check}
grade_result(
  pass_if(~identical(.result, 50*2))
)
```

$$\frac{27}{4}$$

```{r ex-division, exercise=TRUE}

```

<div id="ex-division-hint">
**Hint:** It might be a good idea to search for something like 'division in R' in the web.
</div>

```{r ex-division-check}
grade_result(
  pass_if(~identical(.result, 27/4))
)
```

$$500-650$$

```{r ex-substraction, exercise=TRUE}

```

<div id="ex-substraction-hint">
**Hint:** It might be a good idea to search for something like 'substraction in R' in the web.
</div>

```{r ex-substraction-check}
grade_result(
  pass_if(~identical(.result, 500-650))
)
```

$$2^4$$

```{r ex-power, exercise=TRUE}

```

<div id="ex-power-hint">
**Hint:** It might be a good idea to search for something like 'raise to power in R' in the web.
</div>

```{r ex-power-check}
grade_result(
  pass_if(~identical(.result, 2**4))
)
```

$$\sqrt{3}\cdot 60$$

```{r ex-root, exercise=TRUE}

```

<div id="ex-root-hint">
**Hint:** It might be a good idea to search for something like 'root in R' in the web.
</div>

```{r ex-root-check}
grade_result(
  pass_if(~identical(.result, sqrt(3)*60))
)
```

$$50 \cdot (4+2)^3$$

```{r ex-chained, exercise=TRUE}

```

<div id="ex-chained-hint">
**Hint:** It might be a good idea to search for something like 'calculator use r' in the web.
</div>

```{r ex-chained-check}
grade_result(
  pass_if(~identical(.result, 50*(4+2)**3))
)
```

Do the following chain computation in R. Assign a name to each intermediate 
result and then return the overall result.

*Hint: avoid overwriting existing R functions such as `c()` since this can be*
*confusing. Better use, e.g., names such as `var_c` instead.*

\begin{align*}
a &= 10 + 25\\
b &= a \cdot 40\\
c &= b - 100\\
d &= c \cdot 3\\
e &= \sqrt{d}\\
f &= \frac{e}{1000}\\
g &= f^3
\end{align*}

```{r ex-chained-full, exercise=TRUE, exercise.lines=8}

```

<div id="ex-chained-full-hint">
**Hint:** After assigning an intermediate result to a name you can call it 
via this name in the next calculation step. And dont forget to call the final
result in the last line!
</div>

```{r ex-chained-full-check}
a_ <- 10 + 25
b_ <- a_ * 40
c_ <- b_ - 100
d_ <- c_ * 3
e_ <- sqrt(d_)
f_ <- e_ / 1000
g_ <- f_^3

grade_result(
  pass_if(~identical(.result, g_))
)
```

## Functions

### Content quiz

```{r functionquiz}
quiz(
  question(
    "Which of the following statements about functions in R is/are correct?",
    answer("Functions apply a certain routine on an input, thereby producing (almost always) an output.", correct=TRUE),
    answer("Are the R equivalent to mathematical functions and map numbers from one mathematical space into another."),
    answer("Functions facilitate the debugging of your code, especially if they encapsulate routines that use multiple times.", correct=TRUE),
    answer("Functions are difficult to define for yourself, so you should mainly use pre-defined functions and avoid user-written functions whenever possible."),
    answer("As a rule of thumb, whenever you use some code more than twice, you should encapsulate it into a function.", correct=TRUE), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What do we need optional arguments for?",
    answer("They represent the input to a function and are, thus, necessary for the function to produce an output."),
    answer("They usually help us to adjust the routine implemented in the function to the particular case at hand.", correct=TRUE),
    answer("These kind of arguments are unnecessary. Since they are optional its safe to ignore them until you become a more experienced programmer."),
    answer("All arguments to functions are optional in the strict sense, so there is nothing special about them."), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Consider the function `sum()`. What is its main argument?",
    answer("An arbitrary number of numeric or logical atomic vectors", correct=TRUE),
    answer("A single vector containing numerical elements that the function can sum up."),
    answer("A logical vector named `na.rm`, indicating whether the function should ignore missing values when suming up a vector."),
    answer("The name of the vector of which you want to sum up the elements."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Consider the function `sum()`. What is its optional argument?",
    answer("A logical vector named `na.rm`, indicating whether the function should ignore missing values when suming up a vector.", correct=TRUE),
    answer("The name of the vector of which you want to sum up the elements."),
    answer("A single vector containing numerical elements that the function can sum up."),
    answer("The function `sum()` has no optional arguments."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Only optional arguments can be specified by name. Is this true?",
    answer("No, you can also specify mandatory arguments by name, but this is not necessary.", correct=TRUE),
    answer("Yes, mandatory arguments have no name and must be entered in the sequence they are mentioned in the function definition."),
    answer("No, in fact only mandatory arguments can be specified by name, optional arguments are specified by position."),
    answer("Yes, the name of mandatory arguments is only used for documentation purposes."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Variables that are defined within the function body...",
    answer("disappear after the function has been called.", correct=TRUE),
    answer("remain available after calling the function and can be used to check intermediate results."),
    answer("disappear by default, but can be kept if the universal optional argument `keep_int_vars` is set to `TRUE`."), 
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

### Coding exercises

Define a function called `my_var_func` that takes a vector of numbers as an input
and calculates the sample variance. Note that the formula for the variance is:

$$\frac{\sum_i(x_i-\bar{x})^2}{n-1}$$

where $\bar{x}$ is the mean of $x$, and $n$ the number of elements in x.
Note also that $\bar{x}$ can be computed as `mean(x)` and a sum can be 
computed using `sum()`.

Test your function by applying it to the pre-defined input `test_vector`.

```{r ex-deffun-setup}
test_vector <- seq(1, 8, by=0.25)
```

```{r ex-deffun, exercise=TRUE, exercise.lines=8}

```

```{r ex-deffun-hint-1}
my_var_func <- function(x){
  # function body
}
```

```{r ex-deffun-hint-2}
my_var_func <- function(x){
  x_mean <- mean(x)
  # ...
}
```

```{r ex-deffun-hint-3}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  # ...
}
```

```{r ex-deffun-hint-4}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  # ...
}
```

```{r ex-deffun-solution}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  x_var <- sum(squared_dev) / (x_len-1)
  return(x_var)
}
```

```{r ex-deffun-check}
grade_result(
  pass_if(~identical(.result, var(test_vector)))
)
```

Take the function you defined above and document it according to the rules
that you have read about in the tutorial.

```{r ex-docfun, exercise=TRUE, exercise.lines=8}

```

```{r ex-docfun-hint-1}
# Each documentation should contain a short title, a short description, the
# function arguments and the return value.
```

```{r ex-docfun-hint-2}
# The documentation of a function must come immediately before the function
# definition and each line of the documentation starts with `#'`. 
# In the first line you provide a title, which must not be longer than 80 
# characetrs.

# Then, after inserting a blank line you describe what the function does in a bit 
# more detail. Then, you describe each argument by using the decorator `@param` 
# at the beginning of the lines. Finally, after another blank line, you describe 
# the output of the function after starting the line with the decorator `@return`.
```

```{r ex-docfun-solution}
#' Computes the variance of a vector
#' 
#' This function takes a numeric vector as input and computes the sample
#'  variance. It does not work if missing values are presend.
#' @param x An atomic vector of type `double` or `integer`
#' @return The sample variance of `x` as `double`
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  x_var <- sum(squared_dev) / (x_len-1)
  return(x_var)
}
```
