---
title: "Data wrangling II"
author: "Claudius Gräbner-Radkowitsch"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(scales)
library(gradethis)
library(dplyr)
library(tidyr)
library(data.table)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, 
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```

## General remarks

This exercise session is meant to give you the opportunity to practice your
skills in the context of data preparation. The focus will be on data wrangling,
i.e. the transformation of wide and long data sets.

For the following exercises, assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercises
│   Exercises.Rproj    
│
└───data
│   │   education.csv
│   │   poverty_gdp_countries.csv
│   │   poverty_gdp_regions.csv
|   |   renewables_electricity.csv
└───R
    │   myscript.R
```

**Attention:** Due to the way these exercises were created you cannot use
the function `here()`, as you would usually do. Thus, use relative paths from
the project main directory, i.e. the paths you would normally pass to the 
function `here()`.

Also, in the following exercises, please make sure that you return your final data
set, otherwise your solution cannot be evaluated. This means the the following
does not work:

```{r, eval=FALSE, echo=TRUE}
my_solution <- data.frame("a"=1:2, "b"=3:4)
```

Instead, write:

```{r, eval=FALSE, echo=TRUE}
my_solution <- data.frame("a"=1:2, "b"=3:4)
my_solution
```

Or:

```{r, eval=FALSE, echo=TRUE}
data.frame("a"=1:2, "b"=3:4)
```

Finally, whenever your final solution contains a column with years, please 
make sure this column is called `years`, otherwise the automated feedback
does not work.

## Wide and long data I

*Note*: assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercises
│   Exercises.Rproj    
│
└───data
│   │   education.csv
│   │   poverty_gdp_countries.csv
│   │   poverty_gdp_regions.csv
|   |   renewables_electricity.csv
└───R
    │   myscript.R
```

Import the data set `poverty_gdp_regions.csv` and make it tidy. Make sure it
is saved as a `tibble.`

```{r ex-wrang2-1, exercise=TRUE}

```


```{r ex-wrang2-1-hint-1}
data_raw <- data.table::____(____) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-2}
data_raw <- data.table::____(
  file = ____, 
  ____ = ___) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-3}
data_raw <- data.table::fread(
  file = ____, 
  ____ = ___) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-4}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  ____ = ___) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-5}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  ____ = TRUE) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-6}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::____(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-7}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  ____(____
       ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-1-hint-8}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::____(____
       ) %>% 
  tidyr::____(____)

data_tidy
```

```{r ex-wrang2-1-hint-9}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(____
       ) %>% 
  tidyr::____(____)

data_tidy
```

```{r ex-wrang2-1-hint-10}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(____
       ) %>% 
  tidyr::pivot_wider(____)

data_tidy
```

```{r ex-wrang2-1-hint-11}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = ____,
    names_to = ____,
    values_to = ____
    ) %>% 
  tidyr::pivot_wider(____)

data_tidy
```

```{r ex-wrang2-1-hint-12}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = ____,
    values_to = ____
    ) %>% 
  tidyr::pivot_wider(____)

data_tidy
```

```{r ex-wrang2-1-hint-13}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  tidyr::pivot_wider(____)

data_tidy
```

```{r ex-wrang2-1-hint-14}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  tidyr::pivot_wider(
    names_from = ____, 
    values_from = ____)

data_tidy
```

```{r ex-wrang2-1-hint-15}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv", 
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = ____)

data_tidy
```

```{r ex-wrang2-1-solution}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_regions.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value")

data_tidy
```


```{r ex-wrang2-1-check}
wrang_2_1_sol <- data.table::fread(
  file = "data/poverty_gdp_regions.csv",
  header = TRUE) %>% 
  tibble::as_tibble() %>% 
  tidyr::pivot_longer(
    cols = -c("country", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value")

grader <- grade_this({
  
  if ( stringr::str_detect(.user_code, "here\\(")){
    fail(message = paste0(
      "Your code should not use the function `here::here()`, although ",
      "you should usually use this function. But for the sake of this ",
      "exercise simply use the relative paths you would usually have ",
      "passed to `here::here()`.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "fread") ){
   fail(message = paste0(
      "You need to use the function `fread()` from the package ",
      "`data.table` to import the data!")
    )
  }
  
  if ( !stringr::str_detect(.user_code, "header") ){
      fail(message = paste0(
        "Have a look at the raw data. For data as this you need to ",
        "use the argument `header` in `data.table::fread()`!")
        )
    }
  
  if ( !stringr::str_detect(.user_code, "pivot_longer") ){
      fail(message = paste0(
        "When making this data tidy, at some point you need to make ",
        "it longer using the respective function from the package ",
        "`tidyr`!")
        )
    }
  
  if ( !stringr::str_detect(.user_code, "pivot_wider")){
    fail(message = paste0(
      "When making this data tidy, at some point you need to make ",
      "it wider using the respective function from the package ",
      "`tidyr`!")
      )
  }
  
  if ( !tibble::is_tibble(.result)){
    fail(message = paste0(
      "Your solution is not a tibble. Did you forget to return it? Or ",
      "did you forget to transform the imported data into a `tibble`? ",
      "The package `tibble` contains a function with which you can ",
      "transform data frames into a `tibble`!")
    )
  }
  
  if (identical(.result, wrang_2_1_sol)){
    pass()
  }

  fail()
})
```

## Wide and long data II

*Note*: assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercises
│   Exercises.Rproj    
│
└───data
│   │   education.csv
│   │   poverty_gdp_countries.csv
│   │   poverty_gdp_regions.csv
|   |   renewables_electricity.csv
└───R
    │   myscript.R
```

Import the data set `poverty_gdp_countries.csv`. 
Make the data set tidy and consider only the observations after 2000 and 
countries from Latin America and the Caribbean.
Make sure it is saved as a `tibble` and does not contain columns that only
have one unique value.

```{r ex-wrang2-2, exercise=TRUE}

```

```{r ex-wrang2-2-hint-1}
data_raw <- ____(____) 

data_tidy <- ____(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-2-hint-2}
data_raw <- data.table::fread(____) 

data_tidy <- ____(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-2-hint-3}
data_raw <- data.table::fread(
  file = ,
   = TRUE) 

data_tidy <- ____(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-2-hint-4}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- ____(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-2-hint-5}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-2-hint-6}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-7}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(____) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-8}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(____) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-9}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = ____, 
    names_to = ____, 
    values_to = ____
  ) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-10}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-11}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(____) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-12}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::____(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-13}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(____) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-14}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(
    names_from = ____, 
    values_from = ____
  ) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-15}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value"
  ) %>% 
  dplyr::____(____)

data_tidy
```

```{r ex-wrang2-2-hint-16}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
  ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value"
  ) %>% 
  dplyr::select(____)

data_tidy
```

```{r ex-wrang2-2-solution}
data_raw <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) 

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value"
    ) %>% 
  dplyr::select(-region)

data_tidy
```

```{r ex-wrang2-2-check}
wrang_2_2_sol <- data.table::fread(
  file = "data/poverty_gdp_countries.csv",
  header = TRUE) %>% 
  tibble::as_tibble(.) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "region", "Indicator"), 
    names_to = "year", 
    values_to = "value"
    ) %>% 
  dplyr::filter(
    year>=2000,
    region == "Latin America & Caribbean"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "Indicator", 
    values_from = "value") %>% 
  dplyr::select(-region)

grader <- grade_this({
  
  if ( stringr::str_detect(.user_code, "here\\(")){
    fail(message = paste0(
      "Your code should not use the function `here::here()`, although ",
      "you should usually use this function. But for the sake of this ",
      "exercise simply use the relative paths you would usually have ",
      "passed to `here::here()`.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "fread") ){
   fail(message = paste0(
      "You need to use the function `fread()` from the package ",
      "`data.table` to import the data!")
    )
  }
  
  if ( !stringr::str_detect(.user_code, "header") ){
      fail(message = paste0(
        "Have a look at the raw data. For data as this you need to ",
        "use the argument `header` in `data.table::fread()`!")
        )
    }
  
  if ( !stringr::str_detect(.user_code, "pivot_longer") ){
      fail(message = paste0(
        "When making this data tidy, at some point you need to make ",
        "it longer using the respective function from the package ",
        "`tidyr`!")
        )
    }
  
  if ( !stringr::str_detect(.user_code, "pivot_wider")){
    fail(message = paste0(
      "When making this data tidy, at some point you need to make ",
      "it wider using the respective function from the package ",
      "`tidyr`!")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "filter") ){
      fail(message = paste0(
        "You need to filter the data with the right function from the ",
        "package `dplyr`!")
        )
  }
  
  if ( !stringr::str_detect(.user_code, "select") ){
      fail(message = paste0(
        "You need to remove columns that only contain a single unique ",
        "value. You can use the function `unique` to search these ",
        "columns, and remove them using `dplyr::select()`!")
        )
  }
  
  if ( "region" %in%  names(.result) ){
      fail(message = paste0(
        "Your result contains the colums `region`, but you were asked to ",
        "keep only countries from the region 'Latin America & Caribbean. ",
        "Thus, this column becomes superflouus. ",
        "You can remove it using `dplyr::select()`!")
        )
  }
  
  if ( !tibble::is_tibble(.result)){
    fail(message = paste0(
      "Your solution is not a tibble. Did you forget to return it? Or ",
      "did you forget to transform the imported data into a `tibble`? ",
      "The package `tibble` contains a function with which you can ",
      "transform data frames into a `tibble`!")
    )
  }
  
  if (identical(.result, wrang_2_2_sol)){
    pass()
  }

  fail()
})
```

## Wide and long data III

*Note*: assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercises
│   Exercises.Rproj    
│
└───data
│   │   education.csv
│   │   poverty_gdp_countries.csv
│   │   poverty_gdp_regions.csv
|   |   renewables_electricity.csv
└───R
    │   myscript.R
```

Import the data set `renewables_electricity.csv`. It contains information
about the share of electricity created from renewable sources.
Make it tidy, filter out any missing values, only keep countries from the 
region 'Europe & Central Asia', and remove all columns that contain only
one unique value. Also, information about the share of renawable electricity
should be in a column called `'RenewableElectricity'`.
Finally, make sure the data is saved as a `tibble` .

```{r ex-wrang2-3, exercise=TRUE}

```

```{r ex-wrang2-3-hint-1}
data_raw <- ____(____)

data_tidy <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-2}
data_raw <- data.table::fread(____)

data_tidy <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-3}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-4}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-5}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-6}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::____(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-7}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(____) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-8}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    ____ = ____, 
    ____ = ____, 
    ____ = ____
  ) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-9}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = ____, 
    names_to = ____, 
    values_to = ____
  ) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-10}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = ____, 
    values_to = ____
  ) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-11}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = ____
  ) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-12}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
  ) %>% 
  ____(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-13}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
  ) %>% 
  dplyr::filter(____) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-14}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
  ) %>% 
  dplyr::filter(
    region == ____,
    !____(____)
  ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-15}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
  ) %>% 
  dplyr::filter(
    region == "Europe & Central Asia",
    !is.na(RenewableElectricity)
  ) %>% 
  ____(____)

data_tidy
```

```{r ex-wrang2-3-hint-16}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
  ) %>% 
  dplyr::filter(
    region == "Europe & Central Asia",
    !is.na(RenewableElectricity)
  ) %>% 
  dplyr::select(____)

data_tidy
```

```{r ex-wrang2-3-solution}
data_raw <- data.table::fread(
  file = "data/renewables_electricity.csv")

data_tidy <- tibble::as_tibble(data_raw) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
    ) %>% 
  dplyr::filter(
    region == "Europe & Central Asia",
    !is.na(RenewableElectricity)
    ) %>% 
  dplyr::select(-region)

data_tidy
```

```{r ex-wrang2-3-check}
wrang_2_3_sol <- data.table::fread(
  file = "data/renewables_electricity.csv") %>% 
  tibble::as_tibble(.) %>% 
  tidyr::pivot_longer(
    cols = -c("country", "year"), 
    names_to = "region", 
    values_to = "RenewableElectricity"
    ) %>% 
  dplyr::filter(
    region == "Europe & Central Asia",
    !is.na(RenewableElectricity)
    ) %>% 
  dplyr::select(-region)

grader <- grade_this({
  
  if ( stringr::str_detect(.user_code, "here\\(")){
    fail(message = paste0(
      "Your code should not use the function `here::here()`, although ",
      "you should usually use this function. But for the sake of this ",
      "exercise simply use the relative paths you would usually have ",
      "passed to `here::here()`.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "fread") ){
   fail(message = paste0(
      "You need to use the function `fread()` from the package ",
      "`data.table` to import the data!")
    )
  }
  
  if ( !stringr::str_detect(.user_code, "pivot_longer") ){
      fail(message = paste0(
        "When making this data tidy, at some point you need to make ",
        "it longer using the respective function from the package ",
        "`tidyr`!")
        )
    }
  
  if ( !stringr::str_detect(.user_code, "filter") ){
      fail(message = paste0(
        "You need to filter the data with the right function from the ",
        "package `dplyr`!")
        )
  }
  
  if ( !stringr::str_detect(.user_code, "select") ){
      fail(message = paste0(
        "You need to remove columns that only contain a single unique ",
        "value. You can use the function `unique` to search these ",
        "columns, and remove them using `dplyr::select()`!")
        )
  }
  
  if ( !"RenewableElectricity" %in%  names(.result) ){
      fail(message = paste0(
        "You were asked to save the information about the share of electricity ",
        "in a column called `RenewableElectricity`. You might use ",
        "dplyr::rename() or set the right name when using tidyr::pivot_longer()!")
        )
  }
  
  if ( "region" %in%  names(.result) ){
      fail(message = paste0(
        "Your result contains the colums `region`, but you were asked to ",
        "keep only countries from the region 'Latin America & Caribbean. ",
        "Thus, this column becomes superflouus. ",
        "You can remove it using `dplyr::select()`!")
        )
  }

  if ( sum(is.na(.result))>0 ){
      fail(message = paste0(
        "You still need to filter out missing values. Use `is.na()` ",
        "within `dplyr::filter()` to do so!")
        )
  }
  if ( !tibble::is_tibble(.result)){
    fail(message = paste0(
      "Your solution is not a tibble. Did you forget to return it? Or ",
      "did you forget to transform the imported data into a `tibble`? ",
      "The package `tibble` contains a function with which you can ",
      "transform data frames into a `tibble`!")
    )
  }
  
  if (identical(.result, wrang_2_3_sol)){
    pass()
  }

  fail()
})
```


## Wide and long data IV

*Note*: assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercises
│   Exercises.Rproj    
│
└───data
│   │   education.csv
│   │   poverty_gdp_countries.csv
│   │   poverty_gdp_regions.csv
|   |   renewables_electricity.csv
└───R
    │   myscript.R
```

Import the data set `education.csv` and compute average values for the period 
after 2000 for the different regions. Then make sure the resulting data set is 
saved as a `tibble` and each region has its own column.

*Note:* This means you are not asked to return a tidy data set!

```{r ex-wrang2-4, exercise=TRUE}

```

```{r ex-wrang2-4-hint-1}
data_raw <- ____(____)

data_final <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_final
```

```{r ex-wrang2-4-hint-2}
data_raw <- data.table::fread(____)

data_final <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_final
```

```{r ex-wrang2-4-hint-3}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- ____(____) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_final
```

```{r ex-wrang2-4-hint-4}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::____(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_final
```

```{r ex-wrang2-4-hint-5}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  ____(____) %>% 
  ____(____) %>% 
  ____(____)

data_final
```

```{r ex-wrang2-4-hint-6}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::____(____) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-7}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(____) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-8}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::____(____) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-9}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(____) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-10}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=____(____), 
    ____ = c("region", "Indicator")
  ) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-11}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    ____ = c("region", "Indicator")
  ) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-12}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
  ) %>% 
  tidyr::____(____)

data_final
```

```{r ex-wrang2-4-hint-13}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
  ) %>% 
  tidyr::pivot_wider(____)

data_final
```

```{r ex-wrang2-4-hint-14}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
  ) %>% 
  tidyr::pivot_wider(
    names_from = ____, 
    values_from = ____)

data_final
```

```{r ex-wrang2-4-hint-15}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
  ) %>% 
  tidyr::pivot_wider(
    names_from = "region", 
    values_from = ____)

data_final
```

```{r ex-wrang2-4-solution}
data_raw <- data.table::fread(
  file = "data/education.csv")

data_final <- tibble::as_tibble(data_raw) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
    ) %>% 
  tidyr::pivot_wider(
    names_from = "region", 
    values_from = "Value")

data_final
```

```{r ex-wrang2-4-check}
wrang_2_4_sol <- data.table::fread(
  file = "data/education.csv") %>% 
  tibble::as_tibble(.) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::summarise(
    Value=mean(Value), 
    .by = c("region", "Indicator")
    ) %>% 
  tidyr::pivot_wider(
    names_from = "region", 
    values_from = "Value")

wrang_2_4_sol_alt <- data.table::fread(
  file = "data/education.csv") %>% 
  tibble::as_tibble(.) %>% 
  dplyr::filter(year>=2000) %>% 
  dplyr::group_by(region, Indicator) %>% 
  dplyr::summarise(
    Value=mean(Value), .groups = "drop"
    ) %>% 
  tidyr::pivot_wider(
    names_from = "region", 
    values_from = "Value")


grader <- grade_this({
  
  if ( stringr::str_detect(.user_code, "here\\(")){
    fail(message = paste0(
      "Your code should not use the function `here::here()`, although ",
      "you should usually use this function. But for the sake of this ",
      "exercise simply use the relative paths you would usually have ",
      "passed to `here::here()`.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "fread") ){
   fail(message = paste0(
      "You need to use the function `fread()` from the package ",
      "`data.table` to import the data!")
    )
  }
  
  if ( !stringr::str_detect(.user_code, "filter") ){
      fail(message = paste0(
        "You need to filter the data with the right function from the ",
        "package `dplyr`!")
        )
  }
  
  if ( !stringr::str_detect(.user_code, "summari") ){
      fail(message = paste0(
        "You need to summarize the data with the right function from the ",
        "package `dplyr`!")
        )
  }
  
  if ( !(stringr::str_detect(.user_code, "\\.by") | stringr::str_detect(.user_code, "group_by")) ){
      fail(message = paste0(
        "You need to group the data when summarizing it. You can use ",
        "`dplyr::group_by()` or the `.by` argument in `dplyr::summarize()`.")
        )
  }
  
  if ( !stringr::str_detect(.user_code, "pivot_wider")){
    fail(message = paste0(
      "When making this data tidy, at some point you need to make ",
      "it wider using the respective function from the package ",
      "`tidyr`!")
      )
  }
  
  if (dplyr::is_grouped_df(.result) ){
    fail(message = paste0(
      "Your final data is still grouped. You need to ungroup it!")
      )
  }

  if ( !tibble::is_tibble(.result)){
    fail(message = paste0(
      "Your solution is not a tibble. Did you forget to return it? Or ",
      "did you forget to transform the imported data into a `tibble`? ",
      "The package `tibble` contains a function with which you can ",
      "transform data frames into a `tibble`!")
    )
  }
  
  if ( identical(.result, wrang_2_4_sol) | identical(.result, wrang_2_4_sol_alt) ){
    pass()
  }

  fail()
})
```
