---
title: "Exercises 3: Object types - factors and data frames"
author: "Introduction to data science: session 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tibble)
library(stringr)
library(dplyr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```


## General remarks
*You should complete these exercises at least once before the next lecture.*
*In case you do not understand a solution, please make a post on the course*
*homepage and discuss your problems with the other participants. In case this*
*does not help we can take up the problem in the next session. Please note that*
*feedback on the exercises is highly welcome!*

## Content quiz

```{r factordataquiz}
quiz(
  question(
    "A factor is built upon...",
    answer('the integer type', correct = TRUE),
    answer('the character type'),
    answer('the double type'),
    answer('the numeric type'),
    answer('the data.frame type'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "A data.frame is built upon...",
    answer('the list type', correct = TRUE),
    answer('the integer type'),
    answer('the character type'),
    answer('the double type'),
    answer('the numeric type'),
    answer('the factor type'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What distinguishes a data.frame from a list?",
    answer(
      'The elements of a list can have different lengths, the elements of data.frames cannot.', 
      correct = TRUE),
    answer("A list can contain elements of different types, data.frames cannot."),
    answer("A data.frame is used to store data, but lists are used to store objects."),
    answer("The elements of lists can be names, that of data.frames cannot."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Which of the following is true about the difference between data.frames and tibbles?",
    answer(
      'They behave differently when being printed on screen.', 
      correct = TRUE),
    answer(
      'Tibbles issue a warning when you try to extract a non-existing column, data.frames do not.', 
      correct = TRUE),
    answer(
      'Data frames encourage the use of row names, tibbles encourage not to use them.', 
      correct = TRUE),
    answer('Tibbles can contain larger amounts of data.'),
    answer("Tibbles are an updated version of the data.frame and basically replaced them."),
    answer('Tibbles and data.frames are essentially the same, but originate from different dialects.'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What is the distinctive feature of a factor?",
    answer(
      'It can only contain a pre-specified number of element values.', 
      correct = TRUE),
    answer('It stores words in a more memory-efficient way.'),
    answer("It can be used to store ordinal and interval data."),
    answer("It is the only vector type that can store categorial variables."),
    answer("It is the only vector type that can contain different types of data."),
    allow_retry = TRUE, random_answer_order = TRUE
  )
)
```

## Coding exercise 

Create a factor that contains the elements `1`, `-2`, and `99`, and which 
allows for the levels `1`, `2`, `-2`, `99`, and `-99`.

```{r ex-fac1, exercise=TRUE}

```

```{r ex-fac1-hint-1}
____(_____, levels = c(_____))
```

```{r ex-fac1-hint-2}
____(c(1, -2, 99), levels = c(_____))
```

```{r ex-fac1-hint-3}
factor(c(1, -2, 99), levels = c(_____))
```

```{r ex-fac1-solution}
factor(c(1, -2, 99), levels = c(1, 2, -2, 99, -99))
```

```{r ex-fac1-check}
grade_this({
  fail_if(!is.factor(.result), 
          message = paste0(
            "You did not define a factor, but a {typeof(.result)}.",
            "Use the function `factor` to create a factor!"
            )
          )
  fail_if(!setequal(levels(.result), 
                    as.character(c(1, 2, -2, 99, -99))), 
          message = paste0(
            "There is a problem with the levels you defined!"
            )
          )
  pass_if(identical(.result, factor(c(1, -2, 99), levels = c(1, 2, -2, 99, -99))))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the function `factor()`. ", 
            "You can access define the elements first, and then set the levels "
        )
      )
    )
  fail()
}
)
```

Create a factor that contains the elements:
two times `good`, two times `medium`, and four times `bad`.
The levels should be ordered and include `good`, `medium`, and `bad` with
`good` being the highest rank, and `bad` the lowest.

```{r ex-fac2, exercise=TRUE}

```

```{r ex-fac2-hint-1}
factor(c(____), 
       levels = c(____), ____ = TRUE)
```

```{r ex-fac2-hint-2}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c(____), ____ = TRUE)
```

```{r ex-fac2-hint-3}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ____ = TRUE)
```

```{r ex-fac2-hint-4}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-hint-5}
factor(c(rep("good", 2), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-solution}
factor(c(rep("good", 2), rep("medium", 2), rep("bad", 4)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-check}
grade_this({
  fail_if(!is.factor(.result), 
          message = paste0(
            "You did not define a factor, but a {typeof(.result)}.",
            "Use the function `factor` to create a factor!"
            )
          )
  fail_if(!setequal(levels(.result), c("bad","medium", "good")), 
          message = paste0(
            "There is a problem with the levels you defined! They should ",
            "be `'bad'`, `'medium'`, and `'good'`, ",
            "not {paste(levels(.result), collapse=', ')}!"
            )
          )
  fail_if(!is.ordered(.result), 
          message = paste0("Your factor is not ordered. ",
                           "Use the optional argument `ordered`."))
  pass_if(identical(.result, 
                    factor(c(rep("good", 2), rep("medium", 2), rep("bad", 4)), 
                           levels = c("bad", "medium", "good"), 
                           ordered = TRUE)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the function `factor()` and ", 
            "the optional arguments `levels` and `ordered`."
        )
      )
    )
  fail()
}
)
```

Consider the factor `f_1`. Compute the relative frequencies of its elements.
```{r ex-fac3-setup}
f_1 <- factor(c(
  rep("E1", 4),
  rep("E2", 1),
  rep("E3", 2),
  rep("E4", 7)
  )
)
```

```{r ex-fac3, exercise=TRUE}

```

```{r ex-fac3-hint-1}
____(f_1)/____(f_1)
```

```{r ex-fac3-hint-2}
table(f_1)/____(f_1)
```

```{r ex-fac3-solution}
table(f_1)/length(f_1)
```

```{r ex-fac3-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "table")<1, 
          message = paste0(
            "Your solution should include the function `table()`.", 
            "It allows you to compute absolute frequencies of the factor elements.")
          )
  fail_if(stringr::str_count(.user_code, "length")<1, 
          message = paste0(
            "Your solution should include the function `length()`.", 
            "You can combine it with `table()` to get relative instead of ",
            "absolute frequencies of the elements.")
          )
  pass_if(identical(.result, table(f_1)/length(f_1)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the functions `table()` and ", 
            "`length()`."
        )
      )
    )
  fail()
}
)
```

Consider the three vectors `v_1`, `v_2`, and `v_3`. Create a `data.frame` that
has these three vectors as columns, and where the columns have the headers
`vec_1`, `vec_2`, and `vec_3`.

```{r ex-fac4-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
```

```{r ex-fac4, exercise=TRUE}

```

```{r ex-fac4-hint-1}
data.frame(____)
```

```{r ex-fac4-hint-2}
data.frame(____=____, ____=____, ____=____)
```

```{r ex-fac4-hint-3}
data.frame(____=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac4-hint-4}
data.frame("vec_1"=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac4-solution}
data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac4-check}
grade_this({
  fail_if(is_tibble(.result), 
          message = paste0(
            "You created a `tibble`, not a `data.frame`.")
          )
  fail_if(!is.data.frame(.result), 
          message = paste0(
            "Your solution should be a `data.frame`. It is of type ",
            "{typeof(.result)}, however. Make sure you use the adequate ", 
            "function to create a `data.frame`.")
          )
  fail_if(!setequal(names(.result), 
                    names(data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3))), 
          message = paste0(
            "There is a problem with the names of your `data.frame`. They should ",
            "be `'vec_1'`, `'vec_2'`, and `'vec_3'`, ",
            "not {paste(names(.result), collapse=', ')}!"
            )
          )
  pass_if(identical(.result, data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)))
  fail()
}
)
```

Repeat the previous task, but this time create a `tibble` instead of a 
`data.frame`.

```{r ex-fac5-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
```

```{r ex-fac5, exercise=TRUE}

```

```{r ex-fac5-hint-1}
tibble(____)
```

```{r ex-fac5-hint-2}
tibble(____=____, ____=____, ____=____)
```

```{r ex-fac5-hint-3}
tibble(____=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac5-hint-4}
tibble("vec_1"=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac5-solution}
tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac5-check}
grade_this({
  fail_if(is.data.frame(.result) & !is_tibble(.result), 
          message = paste0(
            "You created a `data.frame`, not a `tibble`.")
          )
  fail_if(!is_tibble(.result), 
          message = paste0(
            "Your solution should be a `tibble`. It is of type ",
            "{typeof(.result)}, however. Make sure you use the adequate ", 
            "function to create a `tibble`.")
          )
  fail_if(!setequal(names(.result), 
                    names(data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3))), 
          message = paste0(
            "There is a problem with the names of your `tibble`. They should ",
            "be `'vec_1'`, `'vec_2'`, and `'vec_3'`, ",
            "not {paste(names(.result), collapse=', ')}!"
            )
          )
  pass_if(identical(.result, tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)))
  fail()
}
)
```

Consider the `tibble` `tib_1`.
Get an overview over its content by applying the function `glimpse` from the 
package `dplyr`. Make sure you call the function such that it becomes immediately
clear from your code that it belongs to this package.

```{r ex-fac6-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac6, exercise=TRUE}

```

```{r ex-fac6-hint-1}
____(____)
```

```{r ex-fac6-hint-2}
____(tib_1)
```

```{r ex-fac6-hint-3}
____::____(tib_1)
```

```{r ex-fac6-hint-4}
____::glimpse(tib_1)
```

```{r ex-fac6-solution}
dplyr::glimpse(tib_1)
```

```{r ex-fac6-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "glimpse")<1, 
          message = paste0(
            "Your solution should include the function `glimpse()`.")
          )
  fail_if(stringr::str_count(.user_code, "dplyr")<1, 
          message = paste0(
            "Your solution should make clear that the function `glimpse()`",
            "comes from the package `dplyr`.")
          )
  pass_if(identical(.result, dplyr::glimpse(tib_1)))
  fail()
}
)
```

Consider again the `tibble` `tib_1`.
Extract the column `vec_2` such that the result is a `tibble`.

```{r ex-fac7-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac7, exercise=TRUE}

```

```{r ex-fac7-hint-1}
____[____]
```

```{r ex-fac7-hint-2}
tib_1[____]
```

```{r ex-fac7-solution}
tib_1["vec_2"]
```

```{r ex-fac7-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "\\[\\["), 
          message = paste0(
            "Remember the two ways you can extract an element from the tibble ",
            "using square brackets. You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "tib_1"), 
          message = paste0(
            "Your solution must refer to the tibble `tib_1`!"
            )
          )
  fail_if(!(stringr::str_detect(.user_code, "\\[2") | 
              stringr::str_detect(.user_code, '\\["vec_2"')), 
          message = paste0(
            "You must refer to the second column in your solution!"
            )
          )
  pass_if(identical(.result, tib_1["vec_2"]))
  fail()
}
)
```

Consider again the `tibble` `tib_1`.
Now extract column `vec_1` such that the result is an atomic vector.

```{r ex-fac8-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac8, exercise=TRUE}

```

```{r ex-fac8-hint-1}
____[[____]]
```

```{r ex-fac8-hint-2}
tib_1[[____]]
```

```{r ex-fac8-solution}
tib_1[["vec_1"]]
```

```{r ex-fac8-check}
grade_this({
  fail_if(
    stringr::str_starts(.user_code, 'tib_1\\["') | 
      stringr::str_starts(.user_code, 'tib_1\\[2'),
    message = paste0(
      "Remember the two ways you can extract an element from the tibble ",
      "using square brackets. You chose the wrong one!"
      )
    )
  fail_if(!stringr::str_detect(.user_code, "tib_1"), 
          message = paste0(
            "Your solution must refer to the tibble `tib_1`!"
            )
          )
  fail_if(!(stringr::str_detect(.user_code, "\\[1") | 
              stringr::str_detect(.user_code, '\\["vec_1"')), 
          message = paste0(
            "You must refer to the first column in your solution!"
            )
          )
  pass_if(identical(.result, tib_1[["vec_1"]]))
  fail()
}
)
```
