---
title: "Exercises: Quarto"
author: "Claudius Gräbner-Radkowitsch"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```

## General remarks

* There will be no coding exercises in the exercise sheet; you can find a link 
to coding exercises in the material section of the course homepage
* The questions and practical tasks all refer to *Quarto*; for a tutorial 
on Markdown (that also includes exercises), please use the 
[CommonMark markdown tutorial](https://commonmark.org/help/tutorial/)

## Content quiz

```{r markdownquiz1}
quiz(
  question(
    "What is true about the relationship between Quarto and R Markdown?",
    answer("Quarto is meant as the 'next-generation' version of R Markdown.", correct = TRUE),
    answer("Quarto is meant to substitute R Markdown in the near future"),
    answer("While R Markdown only supports R for statistical analysis, Quarto supports more languages, such as Julia or Python.", correct = TRUE),
    answer("Quarto is mainly used for writing text, R Markdown for statistical analysis"),
    allow_retry = TRUE, random_answer_order = TRUE),
  
  question(
    "What is the specific feature of Quarto that makes it so attractive?", 
    answer(paste0(
      "It allows writing documents comprising of both R code for statistical ",
      "analysis and Markdown code for formatting text."), 
      correct = TRUE),
    answer("It allows to create graphics interactively."),
    answer("It facilitates the writing of texts in LaTeX from within an R project."),
    answer(paste0(
      "It makes writing R code easier by providing several useful Addins ", 
      "for R-Studio that speeed up common coding tasks.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  
  question("What is the header of a Quarto document used for?",
    answer("It specifies general document properties and determines how the document gets rendered",
           correct = TRUE),
    answer("It can be used to set the default values for the R chunks used in the document",
           correct = TRUE),
    answer("It fixes the meta-data for the rendered documents"),
    answer("It is used to specify the languages that can be used within the documents"),
    allow_retry = TRUE, random_answer_order = TRUE),
  
  question(paste0(
    "Assuming I want to hide the R code in the rendered document, but ", 
    "still include the output it produces, which chunk option should I use?"),
    answer("`echo: false`", correct = TRUE),
    answer("`include: false`"),
    answer("`echo: true`"),
    answer("`hide: true`"),
    answer("`eval: false`"),
    allow_retry = TRUE, random_answer_order = TRUE),
  
  question("What can you control via the chunk option `include`?",
    answer("Whether code and output should be printed in the final documents", correct = TRUE),
    answer("Whether a chunk should be executed during the rendering process"),
    answer("Whether the output of a chunk should be included in the final documents"),
    answer("Whether the objects defined in the chunk should remain in the working environment"),
    allow_retry = TRUE, random_answer_order = TRUE),
  
  question(paste0(
    "When you render a Quarto document, the working directoy used " ,
    "to evaluate relative paths is..."),
    answer("The location of the `.qmd`-file.", correct = TRUE),
    answer("The location of the `.Rproj`-file."),
    answer("The root directory of your computer."),
    answer("The working directory of the current R project."),
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

Consider the following header:

```
title: "Test Markdown"
author: "Claudius"
format: 
  html: 
    toc: true
    toc-depth: 2
    toc-location: body
    number-sections: true
    theme: darkly
  pdf:
    number-sections: true
```

```{r markdownquiz2}
quiz(
  question(
    "Will the rendered document feature a table of contents?",
    answer("Only if you produce an html file", correct = TRUE),
    answer("Yes"),
    answer("No"),
    answer("Only if the document is published as a Netlify webpage"),
    allow_retry = TRUE, random_answer_order = TRUE),
  question("What is the effect of `number-sections: true`?",
    answer("Section headings are numbered", correct = TRUE),
    answer("Section headings can contain numbers"),
    answer("You can allow to use any number of sections you like"),
    allow_retry = TRUE, random_answer_order = TRUE),
  question("What is the effect of `theme: darkly`?",
    answer(paste0("It changes the overall appearence of the resulting file ",
                  "according to a Quarto-theme"), correct = TRUE),
    answer("It chooses a combination of fonts that give a dark appearance"),
    answer("It darkens your code in the resulting html file"),
    answer("It chooses a dark color-coding of the code for your editor"),
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

Consider the following two chunk options:

A)
```
{r, label="make-plot", echo=FALSE, fig.with=8, fig.height=6, warning=FALSE, fig.cap="A nice plot"}
```

B)

```
{r}
#| label: make-plot
#| echo: false
#| fig-width: 8
#| fig-height: 6
#| warning: false
#| fig-cap: "A nice plot"
```

*Note: if you have trouble with the second question, check* 
[this page](https://quarto.org/docs/reference/cells/cells-knitr.html)*.*

```{r markdownquiz3}
quiz(
  question(
    "What is true about their relationship?",
    answer("They have equivalent effects, but the second option is newer and should be preferred", correct = TRUE),
    answer("They have equivalent effects, but the first option is newer and should be preferred"),
    answer("The first only applies to the chunk in question, the second applied globally"),
    answer("The first one works in R Markdown, the second in Quarto"),
    answer("They intend to achieve the same, but the second one does not work because one must use boolean values (`TRUE` instead of `true`)."),
    allow_retry = TRUE, random_answer_order = TRUE),
  question("What are the effects of the chunk options chosen?",
    answer("The chunk output can be referred to via the label 'make-plot'", correct = TRUE),
    answer("The code is not shown in the rendered output, only the results", correct = TRUE),
    answer("The results produced by the code are supressed in the rendered output, but the code itself is shown"),
    answer("The produced figures are 8cm wide and 6cm high"),
    answer("The produced figures are 8 inches wide and 6 inches high", correct = TRUE),
    answer("The produced figures will be accompanied by a caption ('A nice plot)'", correct = TRUE),
    answer("Any warnings produced during code execution will not be shown in the rendered document", correct = TRUE),
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

