---
title: "Exercises 2: Object types"
author: "Introduction to data science: session 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tibble)
library(stringr)
library(dplyr)
gradethis::gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```


## General remarks
*You should complete these exercises at least once before the next lecture.*
*In case you do not understand a solution, please make a post on the course*
*homepage and discuss your problems with the other participants. In case this*
*does not help we can take up the problem in the next session. Please note that*
*feedback on the exercises is highly welcome!*

## Atomic vectors and lists - Content quiz

```{r vectorlistquiz}
quiz(
  question(
    "What is the difference between atomic vectors and lists?",
    answer(
      'Atomic vectors consist of objects of the same types, lists not necessarily.', 
      correct = TRUE),
    answer("Atomic vectors contain single elements, list can also contain longer elements."),
    answer("Atomic vectors store their content in a column, lists in a list format."),
    answer("Atomic vectors can only contain numbers, lists can contain any object type"),
    answer("Atomic vectors are simpler structures that can be the input to functions, something lists cannot be."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
    question(
    "Which of the following types counts as a basic atomic vector type??",
    answer('logical', correct = TRUE),
    answer('integer', correct = TRUE),
    answer('character', correct = TRUE),
    answer('double', correct = TRUE),
    answer('numeric'),
    answer('data.frame'),
    answer('tibble'),
    answer('factor'),
    answer('matrix'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What is the type of "2"',
    answer('logical'),
    answer('integer'),
    answer('character', correct = TRUE),
    answer('double'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'Which of the following functions returns the type of an object?',
    answer('typeof()', correct = TRUE),
    answer('mode()'),
    answer('class()'),
    answer('type()'),
    answer('kind()'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: c(1, 1.6, TRUE)',
    answer('logical'),
    answer('integer'),
    answer('character'),
    answer('double', correct = TRUE),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: as.integer(c(95, 5.2, TRUE))',
    answer('logical'),
    answer('integer', correct = TRUE),
    answer('character'),
    answer('double'),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: c("5", 50, NA)',
    answer('logical'),
    answer('integer', correct = TRUE),
    answer('character'),
    answer('double'),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What does it mean to vectorize an operation?',
    answer(
      'Applying a function to all elements of an atomic vector by applying it to the vector itself.', 
      correct = TRUE),
    answer("Apply an operation to different vectors and store the result in a single vector."),
    answer("Apply an operation to a list and storing the results in a vector"),
    answer("Store several functions in a vector and apply them to a single input at once."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What is the difference between `NULL` and `NA`?',
    answer('`NULL` denotes and absent vector, `NA` an absent element of a vector', correct = TRUE),
    answer("`NULL` is relevant in the context of lists, `NA` in the context of atomic vectors"),
    answer("`NA` denotes a missing value, `NULL` can mean 'zero' both in a numeric and character sense."),
    answer('`NA` denotes a vector that is not available, `NULL` a vector of length zero', correct = TRUE),
    allow_retry = TRUE, random_answer_order = TRUE
  )
)
```
## Atomic vectors and lists - Coding exercise 
 
Create integer with value 10!

```{r ex-createinteger, exercise=TRUE}

```

<div id="ex-createinteger-hint">
**Hint:** There are two ways: using a suffix or applying coercion.
</div>

```{r ex-createinteger-check}
grade_result(
  pass_if(~identical(.result, 10L))
)
```

Test whether the vector `x` is of type `logical`!

```{r ex-testlogical-setup}
x <- "TRUE"
```

```{r ex-testlogical, exercise=TRUE}
____(x)
```

```{r ex-testlogical-solution}
is.logical(x)
```

```{r ex-testlogical-check}
grade_this({
    fail_if_code_feedback(
    message = fail(paste0(
      "Think about the family of functions ",
      "used to test for given types we learned about!")))
  fail()
}
)
```

Coerce the vector `y` into the type `double`

```{r ex-coercedouble-setup}
y <- "1.6"
```

```{r ex-coercedouble, exercise=TRUE}
____(y)
```

```{r ex-coercedouble-solution}
as.double(y)
```

```{r ex-coercedouble-check}
grade_this({
  pass_if(identical(.result, 1.6))
    fail_if_code_feedback(
    message = fail(paste0(
      "Think about the family of functions ", 
      "used to coerce types we learned about!")))
  fail()
}
)
```

The following code computes the square root for the number `1`, `5` and `10` 
one by one. Vectorize it!


```{r ex-vectorizesqrt, exercise=TRUE}
sqrt(1)
sqrt(5)
sqrt(10)
```

```{r ex-vectorizesqrt-solution}
sqrt(c(1, 5, 10))
```

```{r ex-vectorizesqrt-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "sqrt")>1, 
          message = "You should call `sqrt()` only once!")
  pass_if(identical(.result, sqrt(c(1, 5, 10))))
    fail_if_code_feedback(
    message = fail(paste0(
      "To vectorize the operation you need to put all the elements into one ", 
      "atomic vector and then apply the function to it!")))
  fail()
}
)
```

Check out the vector `z`. Compute the fraction of elements that are smaller
than two in a vectorized fashion!

```{r ex-vectorizelogic-setup}
z <- c(1, 5, 6, 2, 9, 20, -4, 0)
```

```{r ex-vectorizelogic, exercise=TRUE}

```

```{r ex-vectorizelogic-hint-1}
____(z____2)/____(z)
```

```{r ex-vectorizelogic-hint-2}
____(z<2)/____(z)
```

```{r ex-vectorizelogic-hint-3}
____(z<2)/length(z)
```

```{r ex-vectorizelogic-solution}
sum(z<2)/length(z)
```

```{r ex-vectorizelogic-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "<")<1, 
          message = paste0(
            "Your solution should include the logical operator `<`! ", 
            "In the end you are interested in how many elements are smaller 2!")
          )
  fail_if(stringr::str_count(.user_code, "sum")<1, 
          message = paste0(
            "Your solution should include the function `sum()`!", 
            "Remember that `TRUE` counts as `1` when summing up logicals!")
          )
  fail_if(stringr::str_count(.user_code, "length")<1, 
          message = paste0(
            "Your solution should include the function `length()`!", 
            "In conjunction with `sum()` it can help you the compute the ",
            "share of elements for which a logical condition is fulfilled.")
          )
  pass_if(identical(.result, sum(z<2)/length(z)))
    fail_if_code_feedback(
    message = fail(paste0(
      "First vectorize the logical test, then sum over the resulting vector, ", 
      "and then divide by the number of elements in the vector (i.e. its length)!")))
  fail()
}
)
```

Create a vector that contains the string `!` 50 times!


```{r ex-rep, exercise=TRUE}

```

```{r ex-rep-hint-1}
____("!")
```

```{r ex-rep-solution}
rep("!", 50)
```

```{r ex-rep-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "rep")<1, 
          message = paste0(
            "We learned about a helper function that creates a vector by repeating ", 
            "a certain string. You may also google for it or check out the tutorial!"
            )
          )
  pass_if(identical(.result, rep("!", 50)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should include the function `rep`! ", 
            "It facilitates the creation of vectors containing the same ",
            " elements. Its  first argument should be `'!`. The secont the ",
            "number of iterations."
        )
      )
    )
  fail()
}
)
```

Create a vector with a sequence from 1 to 50 that has 99 elements and has an
equal step size between elements!

```{r ex-seq, exercise=TRUE}

```

```{r ex-seq-hint-1}
____(1, 50, ____)
```

```{r ex-seq-hint-2}
seq(1, 50, ____)
```

```{r ex-seq-hint-3}
seq(1, 50, ____=99)
```

```{r ex-seq-solution}
seq(1, 50, length.out=99)
```

```{r ex-seq-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, ":"), 
          message = paste0(
            "The shortcut `:` does not help since steps are of length `1`. ",
            "Use a function instead!"
            )
          )
  fail_if(stringr::str_count(.user_code, "seq")<1, 
          message = paste0(
            "We learned about a helper function that creates a sequence of a ", 
            "given length. You may google for it or check out the tutorial!"
            )
          )
  pass_if(identical(.result, seq(1, 50, length.out=99)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should include the function `seq`! ", 
            "It facilitates the creation of sequences. ",
            "The optional argument you are looking for is `length.out`."
        )
      )
    )
  fail()
}
)
```


Consider the vector `a <- c(2, 4, 6)`. Replace its second element with `99`
and print `a` again.

```{r ex-index-setup}
a <- c(2, 4, 6)
```

```{r ex-index, exercise=TRUE}

```

```{r ex-index-hint-1}
a____ <- 99
a
```

```{r ex-index-hint-2}
a[____] <- 99
a
```

```{r ex-index-solution}
a[2] <- 99
a
```

```{r ex-index-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "a<-") | stringr::str_detect(.user_code, "a <-"), 
          message = paste0(
            "You are cheating! Replace the element, do not define the vector anew!"
            )
          )
  fail_if(stringr::str_count(.user_code, "a\\[2\\]")<1, 
          message = paste0(
            "You should replace the second element using the `[` notation."
            )
          )
  pass_if(identical(.result, c(2, 99, 6)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the `[` indexing notation. ", 
            "You can access the second element of `a` via `a[2]` and then ",
            "use the standard assignment tools."
        )
      )
    )
  fail()
}
)
```


Consider the list `l_1`. Extract the second element such that the type of the
extracted object is a `list`.

```{r ex-l1-setup}
l_1 <- list("a"=c(1,2,3), "b"=c("a","b","c"), "c"=c(TRUE, TRUE, FALSE))
```

```{r ex-l1, exercise=TRUE}
l_1
```

<div id="ex-l1-hint">
**Hint:** Think about the two ways you can extract an element from a list (i.e. using either one or two brackets).
</div>


```{r ex-l1-solution}
l_1["b"]
```

```{r ex-l1-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "\\[\\["), 
          message = paste0(
            "Remember the two ways you can extract an element from the list! ",
            "You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "l_1"), 
          message = paste0(
            "Your solution must refer to the list `l_1`!"
            )
          )
  pass_if(identical(.result, l_1["b"]))
  fail()
}
)
```

Consider the list `l_1` again. Extract the second element such that the type of 
the extracted object is an atomic vector.

```{r ex-l2-setup}
l_1 <- list("a"=c(1,2,3), "b"=c("a","b","c"), "c"=c(TRUE, TRUE, FALSE))
```

```{r ex-l2, exercise=TRUE}
l_1
```

<div id="ex-l2-hint">
**Hint:** Think about the two ways you can extract an element from a list (i.e. using either one or two brackets).
</div>


```{r ex-l2-solution}
l_1[["b"]]
```

```{r ex-l2-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, '\\["') | stringr::str_detect(.user_code, '\\[2'),
          message = paste0(
            "Remember the two ways you can extract an element from the list! ",
            "You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "l_1"), 
          message = paste0(
            "Your solution must refer to the list `l_1`!"
            )
          )
  pass_if(identical(.result, l_1[["b"]]))
  fail()
}
)
```

## Factors and data frames - content quiz

```{r factordataquiz}
quiz(
  question(
    "A factor is built upon...",
    answer('the integer type', correct = TRUE),
    answer('the character type'),
    answer('the double type'),
    answer('the numeric type'),
    answer('the data.frame type'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "A data.frame is built upon...",
    answer('the list type', correct = TRUE),
    answer('the integer type'),
    answer('the character type'),
    answer('the double type'),
    answer('the numeric type'),
    answer('the factor type'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What distinguishes a data.frame from a list?",
    answer(
      'The elements of a list can have different lengths, the elements of data.frames cannot.', 
      correct = TRUE),
    answer("A list can contain elements of different types, data.frames cannot."),
    answer("A data.frame is used to store data, but lists are used to store objects"),
    answer("The elements of lists can be names, that of data.frames cannot."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Which of the following is true about the difference between data.frames and tibbles?",
    answer(
      'They behave differently when being printed on screen', 
      correct = TRUE),
    answer(
      'Tibbles issue a warning when you try to extract a non-existing column, data.frames do not', 
      correct = TRUE),
    answer(
      'Data frames encourage the use of row names, tibbles encourage not to use them', 
      correct = TRUE),
    answer('Tibbles can contain larger amounts of data'),
    answer('Tibbles and data.frames are essentially the same, but originate from different dialects'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What is the distinctive feature of a factor?",
    answer(
      'It can only contain a pre-specified number of element values.', 
      correct = TRUE),
    answer('It stores words in a more memory-efficient way.'),
    answer("It can be used to store ordinal and interval data"),
    answer("It is the only vector type that can contain different types of data."),
    allow_retry = TRUE, random_answer_order = TRUE
  )
)
```
## Factors and data frames - coding exercise 

Create a factor that contains the elements `1`, `-2`, and `99`, and which 
allows for the levels `1`, `2`, `-2`, `99`, and `-99`.

```{r ex-fac1, exercise=TRUE}

```

```{r ex-fac1-hint-1}
____(_____, levels = c(_____))
```

```{r ex-fac1-hint-2}
____(c(1, -2, 99), levels = c(_____))
```

```{r ex-fac1-hint-3}
factor(c(1, -2, 99), levels = c(_____))
```

```{r ex-fac1-solution}
factor(c(1, -2, 99), levels = c(1, 2, -2, 99, -99))
```

```{r ex-fac1-check}
grade_this({
  fail_if(!is.factor(.result), 
          message = paste0(
            "You did not define a factor, but a {typeof(.result)}.",
            "Use the function `factor` to create a factor!"
            )
          )
  fail_if(!setequal(levels(.result), 
                    as.character(c(1, 2, -2, 99, -99))), 
          message = paste0(
            "There is a problem with the levels you defined!"
            )
          )
  pass_if(identical(.result, factor(c(1, -2, 99), levels = c(1, 2, -2, 99, -99))))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the function `factor()`. ", 
            "You can access define the elements first, and then set the levels "
        )
      )
    )
  fail()
}
)
```

Create a factor that contains the elements:
two times `good`, two times `medium`, and four times `bad`.
The levels should be ordered and include `good`, `medium`, and `bad` with
`good` being the highest rank, and `bad` the lowest.

```{r ex-fac2, exercise=TRUE}

```

```{r ex-fac2-hint-1}
factor(c(____), 
       levels = c(____), ____ = TRUE)
```

```{r ex-fac2-hint-2}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c(____), ____ = TRUE)
```

```{r ex-fac2-hint-3}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ____ = TRUE)
```

```{r ex-fac2-hint-4}
factor(c(rep(____), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-hint-5}
factor(c(rep("good", 2), rep(____), rep(____)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-solution}
factor(c(rep("good", 2), rep("medium", 2), rep("bad", 4)), 
       levels = c("bad", "medium", "good"), ordered = TRUE)
```

```{r ex-fac2-check}
grade_this({
  fail_if(!is.factor(.result), 
          message = paste0(
            "You did not define a factor, but a {typeof(.result)}.",
            "Use the function `factor` to create a factor!"
            )
          )
  fail_if(!setequal(levels(.result), c("bad","medium", "good")), 
          message = paste0(
            "There is a problem with the levels you defined! They should ",
            "be `'bad'`, `'medium'`, and `'good'`, ",
            "not {paste(levels(.result), collapse=', ')}!"
            )
          )
  fail_if(!is.ordered(.result), 
          message = paste0("Your factor is not ordered. ",
                           "Use the optional argument `ordered`."))
  pass_if(identical(.result, 
                    factor(c(rep("good", 2), rep("medium", 2), rep("bad", 4)), 
                           levels = c("bad", "medium", "good"), 
                           ordered = TRUE)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the function `factor()` and ", 
            "the optional arguments `levels` and `ordered`."
        )
      )
    )
  fail()
}
)
```

Consider the factor `f_1`. Compute the relative frequencies of its elements.
```{r ex-fac3-setup}
f_1 <- factor(c(
  rep("E1", 4),
  rep("E2", 1),
  rep("E3", 2),
  rep("E4", 7)
  )
)
```

```{r ex-fac3, exercise=TRUE}

```

```{r ex-fac3-hint-1}
____(f_1)/____(f_1)
```

```{r ex-fac3-hint-2}
table(f_1)/____(f_1)
```

```{r ex-fac3-solution}
table(f_1)/length(f_1)
```

```{r ex-fac3-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "table")<1, 
          message = paste0(
            "Your solution should include the function `table()`.", 
            "It allows you to compute absolute frequencies of the factor elements.")
          )
  fail_if(stringr::str_count(.user_code, "length")<1, 
          message = paste0(
            "Your solution should include the function `length()`.", 
            "You can combine it with `table()` to get relative instead of ",
            "absolute frequencies of the elements.")
          )
  pass_if(identical(.result, table(f_1)/length(f_1)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the functions `table()` and ", 
            "`length()`."
        )
      )
    )
  fail()
}
)
```

Consider the three vectors `v_1`, `v_2`, and `v_3`. Create a `data.frame` that
has these three vectors as columns, and where the columns have the headers
`vec_1`, `vec_2`, and `vec_3`.

```{r ex-fac4-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
```

```{r ex-fac4, exercise=TRUE}

```

```{r ex-fac4-hint-1}
data.frame(____)
```

```{r ex-fac4-hint-2}
data.frame(____=____, ____=____, ____=____)
```

```{r ex-fac4-hint-3}
data.frame(____=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac4-hint-4}
data.frame("vec_1"=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac4-solution}
data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac4-check}
grade_this({
  fail_if(is_tibble(.result), 
          message = paste0(
            "You created a `tibble`, not a `data.frame`.")
          )
  fail_if(!is.data.frame(.result), 
          message = paste0(
            "Your solution should be a `data.frame`. It is of type ",
            "{typeof(.result)}, however. Make sure you use the adequate ", 
            "function to create a `data.frame`.")
          )
  fail_if(!setequal(names(.result), 
                    names(data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3))), 
          message = paste0(
            "There is a problem with the names of your `data.frame`. They should ",
            "be `'vec_1'`, `'vec_2'`, and `'vec_3'`, ",
            "not {paste(names(.result), collapse=', ')}!"
            )
          )
  pass_if(identical(.result, data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)))
  fail()
}
)
```

Repeat the previous task, but this time create a `tibble` instead of a 
`data.frame`.

```{r ex-fac5-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
```

```{r ex-fac5, exercise=TRUE}

```

```{r ex-fac5-hint-1}
tibble(____)
```

```{r ex-fac5-hint-2}
tibble(____=____, ____=____, ____=____)
```

```{r ex-fac5-hint-3}
tibble(____=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac5-hint-4}
tibble("vec_1"=v_1, ____=v_2, ____=v_3)
```

```{r ex-fac5-solution}
tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac5-check}
grade_this({
  fail_if(is.data.frame(.result) & !is_tibble(.result), 
          message = paste0(
            "You created a `data.frame`, not a `tibble`.")
          )
  fail_if(!is_tibble(.result), 
          message = paste0(
            "Your solution should be a `tibble`. It is of type ",
            "{typeof(.result)}, however. Make sure you use the adequate ", 
            "function to create a `tibble`.")
          )
  fail_if(!setequal(names(.result), 
                    names(data.frame("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3))), 
          message = paste0(
            "There is a problem with the names of your `tibble`. They should ",
            "be `'vec_1'`, `'vec_2'`, and `'vec_3'`, ",
            "not {paste(names(.result), collapse=', ')}!"
            )
          )
  pass_if(identical(.result, tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)))
  fail()
}
)
```

Consider the `tibble` `tib_1`.
Get an overview over its content by applying the function `glimpse` from the 
package `dplyr`. Make sure you call the function such that it becomes immediately
clear from your code that it belongs to this package.

```{r ex-fac6-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac6, exercise=TRUE}

```

```{r ex-fac6-hint-1}
____(____)
```

```{r ex-fac6-hint-2}
____(tib_1)
```

```{r ex-fac6-hint-3}
____::____(tib_1)
```

```{r ex-fac6-hint-4}
____::glimpse(tib_1)
```

```{r ex-fac6-solution}
dplyr::glimpse(tib_1)
```

```{r ex-fac6-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "glimpse")<1, 
          message = paste0(
            "Your solution should include the function `glimpse()`.")
          )
  fail_if(stringr::str_count(.user_code, "dplyr")<1, 
          message = paste0(
            "Your solution should make clear that the function `glimpse()`",
            "comes from the package `dplyr`.")
          )
  pass_if(identical(.result, dplyr::glimpse(tib_1)))
  fail()
}
)
```

Consider again the `tibble` `tib_1`.
Extract the column `vec_2` such that the result is a `tibble`.

```{r ex-fac7-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac7, exercise=TRUE}

```

```{r ex-fac7-hint-1}
____[____]
```

```{r ex-fac7-hint-2}
tib_1[____]
```

```{r ex-fac7-solution}
tib_1["vec_2"]
```

```{r ex-fac7-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "\\[\\["), 
          message = paste0(
            "Remember the two ways you can extract an element from the tibble ",
            "using square brackets. You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "tib_1"), 
          message = paste0(
            "Your solution must refer to the tibble `tib_1`!"
            )
          )
  fail_if(!(stringr::str_detect(.user_code, "\\[2") | 
              stringr::str_detect(.user_code, '\\["vec_2"')), 
          message = paste0(
            "You must refer to the second column in your solution!"
            )
          )
  pass_if(identical(.result, tib_1["vec_2"]))
  fail()
}
)
```

Consider again the `tibble` `tib_1`.
Now extract column `vec_1` such that the result is an atomic vector.

```{r ex-fac8-setup}
v_1 <- 1:4
v_2 <- letters[1:4]
v_3 <- c(TRUE, FALSE, TRUE, FALSE)
tib_1 <- tibble("vec_1"=v_1, "vec_2"=v_2, "vec_3"=v_3)
```

```{r ex-fac8, exercise=TRUE}

```

```{r ex-fac8-hint-1}
____[[____]]
```

```{r ex-fac8-hint-2}
tib_1[[____]]
```

```{r ex-fac8-solution}
tib_1[["vec_1"]]
```

```{r ex-fac8-check}
grade_this({
  fail_if(
    stringr::str_detect(.user_code, '\\["') | 
      stringr::str_detect(.user_code, '\\[2'),
    message = paste0(
      "Remember the two ways you can extract an element from the tibble ",
      "using square brackets. You chose the wrong one!"
      )
    )
  fail_if(!stringr::str_detect(.user_code, "tib_1"), 
          message = paste0(
            "Your solution must refer to the tibble `tib_1`!"
            )
          )
  fail_if(!(stringr::str_detect(.user_code, "\\[1") | 
              stringr::str_detect(.user_code, '\\["vec_1"')), 
          message = paste0(
            "You must refer to the first column in your solution!"
            )
          )
  pass_if(identical(.result, tib_1[["vec_1"]]))
  fail()
}
)
```
