---
title: "Exercises 2: Object types - atomic vectors and lists"
author: "Introduction to data science: session 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tibble)
library(stringr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, fail_code_feedback = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```


## General remarks
*You should complete these exercises at least once before the next lecture.*
*In case you do not understand a solution, please make a post on the course*
*homepage and discuss your problems with the other participants. In case this*
*does not help we can take up the problem in the next session. Please note that*
*feedback on the exercises is highly welcome!*

## Content quiz

```{r vectorlistquiz}
quiz(
  question(
    "What is the difference between atomic vectors and lists?",
    answer(
      'Atomic vectors consist of objects of the same types, lists not necessarily.', 
      correct = TRUE),
    answer("Atomic vectors contain single elements, list can also contain longer elements."),
    answer("Atomic vectors store their content in a column, lists in a list format."),
    answer("Atomic vectors can only contain numbers, lists can contain any object type"),
    answer("Atomic vectors are simpler structures that can be the input to functions, something lists cannot be."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
    question(
    "Which of the following types counts as a basic atomic vector type??",
    answer('logical', correct = TRUE),
    answer('integer', correct = TRUE),
    answer('character', correct = TRUE),
    answer('double', correct = TRUE),
    answer('numeric'),
    answer('data.frame'),
    answer('tibble'),
    answer('factor'),
    answer('matrix'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What is the type of "2"',
    answer('logical'),
    answer('integer'),
    answer('character', correct = TRUE),
    answer('double'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'Which of the following functions returns the type of an object?',
    answer('typeof()', correct = TRUE),
    answer('mode()'),
    answer('class()'),
    answer('type()'),
    answer('kind()'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: c(1, 1.6, TRUE)',
    answer('logical'),
    answer('integer'),
    answer('character'),
    answer('double', correct = TRUE),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: as.integer(c(95, 5.2, TRUE))',
    answer('logical'),
    answer('integer', correct = TRUE),
    answer('character'),
    answer('double'),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What type will this vector have: c("5", 50, NA)',
    answer('logical'),
    answer('integer', correct = TRUE),
    answer('character'),
    answer('double'),
    answer('numeric'),
    answer('factor'),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What does it mean to vectorize an operation?',
    answer(
      'Applying a function to all elements of an atomic vector by applying it to the vector itself.', 
      correct = TRUE),
    answer("Apply an operation to different vectors and store the result in a single vector."),
    answer("Apply an operation to a list and storing the results in a vector"),
    answer("Store several functions in a vector and apply them to a single input at once."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    'What is the difference between `NULL` and `NA`?',
    answer('`NULL` denotes and absent vector, `NA` an absent element of a vector', correct = TRUE),
    answer("`NULL` is relevant in the context of lists, `NA` in the context of atomic vectors"),
    answer("`NA` denotes a missing value, `NULL` can mean 'zero' both in a numeric and character sense."),
    answer('`NA` denotes a vector that is not available, `NULL` a vector of length zero', correct = TRUE),
    allow_retry = TRUE, random_answer_order = TRUE
  )
)
```
## Coding exercise 
 
Create integer with value 10!

```{r ex-createinteger, exercise=TRUE}

```

<div id="ex-createinteger-hint">
**Hint:** There are two ways: using a suffix or applying coercion.
</div>

```{r ex-createinteger-check}
grade_result(
  pass_if(~identical(.result, 10L))
)
```

Test whether the vector `x` is of type `logical`!

```{r ex-testlogical-setup}
x <- "TRUE"
```

```{r ex-testlogical, exercise=TRUE}
____(x)
```

```{r ex-testlogical-solution}
is.logical(x)
```

```{r ex-testlogical-check}
grade_this({
    fail_if_code_feedback(
    message = fail(paste0(
      "Think about the family of functions ",
      "used to test for given types we learned about!")))
  fail()
}
)
```

Coerce the vector `y` into the type `double`

```{r ex-coercedouble-setup}
y <- "1.6"
```

```{r ex-coercedouble, exercise=TRUE}
____(y)
```

```{r ex-coercedouble-solution}
as.double(y)
```

```{r ex-coercedouble-check}
grade_this({
  pass_if(identical(.result, 1.6))
    fail_if_code_feedback(
    message = fail(paste0(
      "Think about the family of functions ", 
      "used to coerce types we learned about!")))
  fail()
}
)
```

The following code computes the square root for the number `1`, `5` and `10` 
one by one. Vectorize it!


```{r ex-vectorizesqrt, exercise=TRUE}
sqrt(1)
sqrt(5)
sqrt(10)
```

```{r ex-vectorizesqrt-solution}
sqrt(c(1, 5, 10))
```

```{r ex-vectorizesqrt-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "sqrt")>1, 
          message = "You should call `sqrt()` only once!")
  pass_if(identical(.result, sqrt(c(1, 5, 10))))
    fail_if_code_feedback(
    message = fail(paste0(
      "To vectorize the operation you need to put all the elements into one ", 
      "atomic vector and then apply the function to it!")))
  fail()
}
)
```

Check out the vector `z`. Compute the fraction of elements that are smaller
than two in a vectorized fashion!

```{r ex-vectorizelogic-setup}
z <- c(1, 5, 6, 2, 9, 20, -4, 0)
```

```{r ex-vectorizelogic, exercise=TRUE}

```

```{r ex-vectorizelogic-hint-1}
____(z____2)/____(z)
```

```{r ex-vectorizelogic-hint-2}
____(z<2)/____(z)
```

```{r ex-vectorizelogic-hint-3}
____(z<2)/length(z)
```

```{r ex-vectorizelogic-solution}
sum(z<2)/length(z)
```

```{r ex-vectorizelogic-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "<")<1, 
          message = paste0(
            "Your solution should include the logical operator `<`! ", 
            "In the end you are interested in how many elements are smaller 2!")
          )
  fail_if(stringr::str_count(.user_code, "sum")<1, 
          message = paste0(
            "Your solution should include the function `sum()`!", 
            "Remember that `TRUE` counts as `1` when summing up logicals!")
          )
  fail_if(stringr::str_count(.user_code, "length")<1, 
          message = paste0(
            "Your solution should include the function `length()`!", 
            "In conjunction with `sum()` it can help you the compute the ",
            "share of elements for which a logical condition is fulfilled.")
          )
  pass_if(identical(.result, sum(z<2)/length(z)))
    fail_if_code_feedback(
    message = fail(paste0(
      "First vectorize the logical test, then sum over the resulting vector, ", 
      "and then divide by the number of elements in the vector (i.e. its length)!")))
  fail()
}
)
```

Create a vector that contains the string `!` 50 times!


```{r ex-rep, exercise=TRUE}

```

```{r ex-rep-hint-1}
____("!")
```

```{r ex-rep-solution}
rep("!", 50)
```

```{r ex-rep-check}
grade_this({
  fail_if(stringr::str_count(.user_code, "rep")<1, 
          message = paste0(
            "We learned about a helper function that creates a vector by repeating ", 
            "a certain string. You may also google for it or check out the tutorial!"
            )
          )
  pass_if(identical(.result, rep("!", 50)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should include the function `rep`! ", 
            "It facilitates the creation of vectors containing the same ",
            " elements. Its  first argument should be `'!`. The secont the ",
            "number of iterations."
        )
      )
    )
  fail()
}
)
```

Create a vector with a sequence from 1 to 50 that has 99 elements and has an
equal step size between elements!

```{r ex-seq, exercise=TRUE}

```

```{r ex-seq-hint-1}
____(1, 50, ____)
```

```{r ex-seq-hint-2}
seq(1, 50, ____)
```

```{r ex-seq-hint-3}
seq(1, 50, ____=99)
```

```{r ex-seq-solution}
seq(1, 50, length.out=99)
```

```{r ex-seq-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, ":"), 
          message = paste0(
            "The shortcut `:` does not help since steps are of length `1`. ",
            "Use a function instead!"
            )
          )
  fail_if(stringr::str_count(.user_code, "seq")<1, 
          message = paste0(
            "We learned about a helper function that creates a sequence of a ", 
            "given length. You may google for it or check out the tutorial!"
            )
          )
  pass_if(identical(.result, seq(1, 50, length.out=99)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should include the function `seq`! ", 
            "It facilitates the creation of sequences. ",
            "The optional argument you are looking for is `length.out`."
        )
      )
    )
  fail()
}
)
```


Consider the vector `a <- c(2, 4, 6)`. Replace its second element with `99`
and print `a` again.

```{r ex-index-setup}
a <- c(2, 4, 6)
```

```{r ex-index, exercise=TRUE}

```

```{r ex-index-hint-1}
a____ <- 99
a
```

```{r ex-index-hint-2}
a[____] <- 99
a
```

```{r ex-index-solution}
a[2] <- 99
a
```

```{r ex-index-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "a<-") | stringr::str_detect(.user_code, "a <-"), 
          message = paste0(
            "You are cheating! Replace the element, do not define the vector anew!"
            )
          )
  fail_if(stringr::str_count(.user_code, "a\\[2\\]")<1, 
          message = paste0(
            "You should replace the second element using the `[` notation."
            )
          )
  pass_if(identical(.result, c(2, 99, 6)))
  fail_if_code_feedback(
    message = fail(
      paste0(
            "Your solution should make use of the `[` indexing notation. ", 
            "You can access the second element of `a` via `a[2]` and then ",
            "use the standard assignment tools."
        )
      )
    )
  fail()
}
)
```


Consider the list `l_1`. Extract the second element such that the type of the
extracted object is a `list`.

```{r ex-l1-setup}
l_1 <- list("a"=c(1,2,3), "b"=c("a","b","c"), "c"=c(TRUE, TRUE, FALSE))
```

```{r ex-l1, exercise=TRUE}
l_1
```

<div id="ex-l1-hint">
**Hint:** Think about the two ways you can extract an element from a list (i.e. using either one or two brackets).
</div>


```{r ex-l1-solution}
l_1["b"]
```

```{r ex-l1-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, "\\[\\["), 
          message = paste0(
            "Remember the two ways you can extract an element from the list! ",
            "You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "l_1"), 
          message = paste0(
            "Your solution must refer to the list `l_1`!"
            )
          )
  pass_if(identical(.result, l_1["b"]))
  fail()
}
)
```

Consider the list `l_1` again. Extract the second element such that the type of 
the extracted object is an atomic vector.

```{r ex-l2-setup}
l_1 <- list("a"=c(1,2,3), "b"=c("a","b","c"), "c"=c(TRUE, TRUE, FALSE))
```

```{r ex-l2, exercise=TRUE}
l_1
```

<div id="ex-l2-hint">
**Hint:** Think about the two ways you can extract an element from a list (i.e. using either one or two brackets).
</div>


```{r ex-l2-solution}
l_1[["b"]]
```

```{r ex-l2-check}
grade_this({
  fail_if(stringr::str_detect(.user_code, '\\["') | stringr::str_detect(.user_code, '\\[2'),
          message = paste0(
            "Remember the two ways you can extract an element from the list! ",
            "You chose the wrong one!"
            )
          )
  fail_if(!stringr::str_detect(.user_code, "l_1"), 
          message = paste0(
            "Your solution must refer to the list `l_1`!"
            )
          )
  pass_if(identical(.result, l_1[["b"]]))
  fail()
}
)
```
