---
title: "Exercises 11: Sampling"
author: "Introduction to data science: session 14"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(dplyr)
library(purrr)
library(stringr)
library(ggplot2)
library(moderndive)
library(ggcheck)

knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)

EUFstudents_fem <- DataScienceExercises::EUFstudents %>% 
  dplyr::filter(Gender=="female") %>% 
  dplyr::select(Height)
```

## Content quiz

```{r quiz}
quiz(
  question(
    "What is the relationship between a 'sample' and a 'population'?", 
    answer(paste0("The sample is a subset of the population."), 
      correct = TRUE),
    answer(paste0("The population is a subset of the sample.")),
    answer(paste0(
      "Samples are merged subsets of different populations, despite being ",
      "used to study only one particular population among them.")),
    answer(paste0("Samples and populations are fully independent concepts.")),
    answer(paste0("A sample is the generalization of a population ",
                  "(e.g. for the purpose of prediction).")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What do mean by 'sample variation'?", 
    answer(paste0(
      "The fact that different random samples from the same population ",
      "differ from each other."), 
      correct = TRUE),
    answer(paste0(
      "That samples consists of different elements, which are typically ",
      "heterogeneous.")),
    answer(paste0("The fact that in order to get representative samples we ",
                  "need to vary the techniques used to gather the sample.")),
    answer(paste0(
      "The variation of sample statistics over different observation periods.")),
    answer(paste0("The variation coefficient of a single sample.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is a 'Monte Carlo Simulation'?", 
    answer(paste0(
      "A simulation that studies a random process by repeating it many times."), 
      correct = TRUE),
    answer(paste0(
      "A simulation to assess the properties of Monte Carlo estimations.")),
    answer(paste0(
      "A kind of simulation that is used to study the sampling ",
      "variation of estimators.")),
    answer(paste0(
      "A simulation that studies deterministic processes ",
      "using probabilistic techniques.")),
    answer(paste0(
      "A simulation that is used to find the right sampling ",
      "methodology for the population of interest.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is a 'population parameter'?", 
    answer(paste0(
      "A statistical property of the population that is of interest."), 
      correct = TRUE),
    answer(paste0(
      "A parameter of the process that has generated the population.")),
    answer(paste0(
      "A parameter that determines how one can sample from a population.")),
    answer(paste0(
      "A parameter to be estimated using a population census.")),
    answer(paste0(
      "A parameter of a population that is used to estimate the sampling variation.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is a 'sample statistic'?", 
    answer(paste0(
      "A statistic computed for the sample and that is to be used to ",
      "estimate a population parameter of interest."), 
      correct = TRUE),
    answer(paste0(
      "An estimate for a given random sample used to estimate sample variation.")),
    answer(paste0(
      "Any statistic describing a property of a sample.")),
    answer(paste0(
      "A statistical property of a population that determines the respective ",
      "properties of its samples.")),
    answer(paste0(
      "A randomly selected statistic that is used to analyse a population.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is a 'sampling distribution'?", 
    answer(paste0("The distribution of a sample statistic."), 
      correct = TRUE),
    answer(paste0("The distribution of a sample.")),
        answer(paste0(
      "The distribution of a sample statistic within a single random sample.")),
    answer(paste0(
      "The random distribution that best describes a given random sample.")),
    answer(paste0(
      "The distribution that best describes the sampling behavior of a researcher.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is a 'standard error'?", 
    answer(paste0(
      "The standard deviation of the sampling distribution ",
      "of a sample statistic."), 
      correct = TRUE),
    answer(paste0(
      "The error that inevitably occurs during every estimation based on ",
      "random samples.")),
    answer(paste0(
      "The standard error of the distribution of estimates for the sample ",
      "variation.")),
    answer(paste0(
      "The standard deviation of a population parameter.")),
    answer(paste0(
      "The variance of a sample statistic of interest.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "When do we say that a sample is 'unbiased'?", 
    answer(paste0(
      "If each member of the population has the same probability ",
      "to become a member of the sample."), 
      correct = TRUE),
    answer(paste0(
      "If results obtained from the sample can be generalized to the ", 
      "population the sample was drawn from.")),
    answer(paste0(
      "If the sample size is large enough for the resulting estimators to be ",
      "unbiased.")),
    answer(paste0(
      "If the sample was drawn randomly.")),
    answer(paste0(
      "If the sample composition resembles that of the underlying population.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is the difference between 'accuracy' and 'precision'?", 
    answer(paste0(
      "Precision refers to the spread of estimates, ", 
      "accuracy to their level of bias."), 
      correct = TRUE),
    answer(paste0("There is no different, the two are synonymous.")),
    answer(paste0(
      "Accuracy refers to how well an estimator avoids bias, precision to ",
      "how well the estimator avoids inconsistency.")),
    answer(paste0(
      "Accuracy measures the difference between the expeceted value of an ",
      "estimator and its true value, precision the variance of the estimator ",
      "and the variance of the population parameter of interest.")),
    answer(paste0(
      "Precision refers to the compuational cost in relation to how well the ",
      "estimator captures the true population parameter, accuracy refers to ",
      "the abolute level of unbiasedness.")),
    allow_retry = TRUE, random_answer_order = TRUE),
  question(
    "What is the central message of the Central Limit Theorem (CLT)?", 
    answer(paste0(
      "When a sample becomes larger, its sampling distribution ",
      "becomes narrower and more normally distributed ",
      "(regardless of the population distribution)."), 
      correct = TRUE),
    answer(paste0(
      "When we draw many samples from the same population, their ",
      "sampling distribution will start resembling the distribution of ",
      "the underlying population.")),
    answer(paste0(
      "When we draw more and more samples from one population, the mean of ",
      "the samples approaches the mean of the underlying population.")),
    answer(paste0(
      "When sample size increases, the standard error of the estimates ",
      "becomes larger.")),
    answer(paste0(
      "Increasing the sample size reduces the bias of any estimate based on ",
      "sample statistics, and an infinitely large sample has a bias of zero.")),
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

## Coding exercises I: iteration via for-loops

Suppose you want to study the sample distribution of a sample statistic,
in the present case the standard deviation of the height of all female students
from the EUF. 

The data set `EUFstudents_fem` contains a census of all female students and
their height. We want to draw 1000 artificial samples from this data and
compute the standard deviation of each sample, and then study the sample 
variation.

### Produce an output container

We decide to implement this task by using a for-loop. Thus, the first step
is to create a container vector that contains 1000 `NA`s. Create this vector,
name it `res_container` and return it.


```{r sampex-1, exercise=TRUE}

```

<div id="sampex-1-hint">
**Hint:** Use the function `rep()` to complete this task.
</div>

```{r sampex-1-solution}
res_container <- rep(NA, 1000)
```


```{r sampex-1-check}
grade_this({
  bare_code <- str_remove_all(as.character(.user_code), " ")
    # Check whether the correct data set has been used
  if (!str_detect(bare_code, "res_container<-")){
    fail("Your call should define an object named 'res_container'!")
    }
  if (!str_detect(bare_code, "rep")){
    fail("Your call should make use of the function 'rep()'!")
    }
  if (identical(.result, rep(NA, 1000))){
    pass()
    }
  fail()
})
```

### Implement the random process

It is always a good idea to first define the random process under scrutiny
in isolation. Thus, start by writing code that draws a random sample of size
20 from the population of all female students at the EUF (which is available
as `EUFstudents_fem`.)

**Note:** *To allow for an evaluation of your solution you need to keep the *
*first line with `set.seed(123)` below!*

```{r sampex-2, exercise=TRUE}
set.seed(123)
```

<div id="sampex-2-hint">
**Hint:** Use the function `sample()` to draw a sample.
</div>

```{r sampex-2-hint-1}
set.seed(123)
sample(____)
```

```{r sampex-2-hint-2}
set.seed(123)
sample(x = ____, size = 20)
```

```{r sampex-2-hint-3}
set.seed(123)
sample(x = EUFstudents_fem[[____]], size = 20)
```

```{r sampex-2-solution}
set.seed(123)
sample(EUFstudents_fem[["Height"]], size = 20)
```

```{r sampex-2-check}
grade_this({
  set.seed(123)
  solution <- sample(EUFstudents_fem[["Height"]], size = 20)
  
  bare_code <- str_remove_all(as.character(.user_code), " ")
    # Check whether the correct data set has been used
  if (!str_detect(bare_code, "EUFstudents_fem")){
    fail("You must refer to the data set 'EUFstudents_fem'!")
    }
  if (!str_detect(bare_code, "Height")){
    fail("You must refer to the column 'Height'!")
    }
  if (!str_detect(bare_code, "sample\\(")){
    fail("You must refer to the function 'sample()'!")
    }
  if (length(.result)!=20){
    fail("Your sample should be of length 20, not {length(.result)}!")
    }
  if (identical(.result, solution)){
    pass()
    }
  fail()
})
```

### Conduct the full MCS

Now you know how to draw a single sample! Now build a for loop that reiterates
the following 1000 times:

* Draw a sample of size 20 as you did in the previous exercise
* Compute the standard deviation for this sample
* Save this standard deviation in the vector `res_container`, which you have
defined above
* Return the vector `res_container`

**Note:** *To allow for an evaluation of your solution you need to keep the *
*first line with `set.seed(123)` below!*

```{r sampex-3-setup}
res_container <- rep(NA, 1000)
```

```{r sampex-3, exercise=TRUE}
set.seed(123)

```

```{r sampex-3-hint-1}
set.seed(123)
for (____){
  ____
}
res_container
```

```{r sampex-3-hint-2}
set.seed(123)
for (i in seq_along(res_container)){
  ____
}
res_container
```

```{r sampex-3-hint-3}
set.seed(123)
for (i in seq_along(res_container)){
  sample_drawn <- ____
  sample_sd <- ____
  res_container____ <- sample_sd
}
res_container
```

```{r sampex-3-hint-4}
set.seed(123)
for (i in seq_along(res_container)){
  sample_drawn <- sample(x = EUFstudents_fem[["Height"]], size = 20)
  sample_sd <- ____
  res_container____ <- sample_sd
}
res_container
```

```{r sampex-3-hint-5}
set.seed(123)
for (i in seq_along(res_container)){
  sample_drawn <- sample(x = EUFstudents_fem[["Height"]], size = 20)
  sample_sd <- sd(____)
  res_container____ <- sample_sd
}
res_container
```

```{r sampex-3-hint-6}
set.seed(123)
for (i in seq_along(res_container)){
  sample_drawn <- sample(x = EUFstudents_fem[["Height"]], size = 20)
  sample_sd <- sd(____)
  res_container[i] <- sample_sd
}
res_container
```

```{r sampex-3-solution}
set.seed(123)
for (i in seq_along(res_container)){
  sample_drawn <- sample(x = EUFstudents_fem[["Height"]], size = 20)
  sample_sd <- sd(sample_drawn)
  res_container[i] <- sample_sd
}
res_container
```

```{r sampex-3-check}
grade_this({
  bare_code <- str_remove_all(as.character(.user_code), " ")
  if (!str_detect(bare_code, "for")){
    fail("You should use a for-loop in your solution!")
    }
  if (!str_detect(bare_code, "EUFstudents_fem")){
    fail("You must refer to the data set 'EUFstudents_fem'!")
    }
  if (!str_detect(bare_code, "Height")){
    fail("You must refer to the column 'Height'!")
    }
  if (!str_detect(bare_code, "sample\\(")){
    fail("You must refer to the function 'sample()'!")
    }
  if (!str_detect(bare_code, "sd\\(")){
    fail(paste0(
      "To compute the standard deviation of the sample you ",
      "must refer to the function 'sd()'!"))
    }
  if (identical(.result, rep(NA, 1000))){
    fail(paste0(
      "You did not alter the vector `res_container`. ",
      "Make sure that the result of each iteration step gets ",
      "stored in this vector!"))
    }
  if (!str_detect(bare_code, "res_container\\[")){
    fail(paste0(
      "In each round of the loop you must store the result ",
      "in `res_container`. Check out vector indexing if you do ",
      "not remember how to do it!"))
  }
  set.seed(123)
  solution <- purrr::map_dbl(
    .x = seq_along(res_container), 
    .f = ~sd(sample(x = EUFstudents_fem[["Height"]], size = 20)))
  if (identical(.result, solution)){
    pass()
    }
  fail()
})
```


## Coding exercises II: iteration using the purrr package

### Rewrite code using the purrr-package

An alternative way to conduct MCS is to use the functions provided by the 
`purrr`-package. Implement the same exercise as you did before, but this time
use the function `purrr::map_dbl()`.

**Note:** *To allow for an evaluation of your solution you need to keep the *
*first line with `set.seed(123)` below!*

```{r sampex-4, exercise=TRUE}
set.seed(123)

```

```{r sampex-4-hint-1}
set.seed(123)
purrr::map_dbl(
  ____
  )
```

```{r sampex-4-hint-2}
set.seed(123)
purrr::map_dbl(
  .x = ____, 
  .f = ____
  )
```

```{r sampex-4-hint-3}
set.seed(123)
purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ____
  )
```

```{r sampex-4-hint-4}
set.seed(123)
purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ~____
  )
```

```{r sampex-4-hint-5}
set.seed(123)
purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ~sd(sample(____))
  )
```

```{r sampex-4-solution}
set.seed(123)
purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ~sd(sample(x = EUFstudents_fem[["Height"]], size = 20))
  )
```

```{r sampex-4-check}
grade_this({
  bare_code <- str_remove_all(as.character(.user_code), " ")
  
  if (!str_detect(bare_code, "map_dbl")){
    fail(paste0(
      "Your call should make use of the ",
      "function `map_dbl()` from the package `purrr`!"))
    }
  set.seed(123)
  solution <- purrr::map_dbl(
    .x = seq_along(res_container), 
    .f = ~sd(sample(x = EUFstudents_fem[["Height"]], size = 20)))
  if (identical(.result, solution)){
    pass()
    }
  fail()
})
```

### Transformation into a tibble

In a last step you should now visualize the result of your MCS using `ggplot2`.
But before you can pass your result to `ggplot2` you must transform it into
a `tibble`. Assume you stored the result of your MCS in the vector `mcs_result`.
Transform this vector into a tibble that can then be passed to 
`ggplot2::ggplot()` and name it `mcs_result_tbl`.

```{r sampex-5-setup}
set.seed(123)
mcs_result <- purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ~sd(sample(x = EUFstudents_fem[["Height"]], size = 20))
  )
```

```{r sampex-5, exercise=TRUE}

```

```{r sampex-5-hint-1}
mcs_result_tbl <- ____(mcs_result)
mcs_result_tbl
```

```{r sampex-5-hint-2}
mcs_result_tbl <- tibble::____(mcs_result)
mcs_result_tbl
```

```{r sampex-5-hint-3}
mcs_result_tbl <- tibble::as____(mcs_result)
mcs_result_tbl
```

```{r sampex-5-solution}
mcs_result_tbl <- tibble::as_tibble(mcs_result)
mcs_result_tbl
```

```{r sampex-5-check}
grade_this({
  bare_code <- str_remove_all(as.character(.user_code), " ")
  
  if (!tibble::is_tibble(.result)){
    fail(paste0(
      "You should produce a `tibble`, but the object you returned is ",
      "'{class(.result)}'. To transform a vector into a tibble use the ",
      "function `as_tibble()` from the package `tibble`!"))
    }
  if (identical(.result, tibble::as_tibble(mcs_result))){
    pass()
    }
  fail()
})
```

### Visualization

Now visualize the results of your MCS using the just defined object 
`mcs_result_tbl`. To this end, create a histogram using `ggplot`, where the 
true value of the population standard variation is marked.

**Hint:** *You can add a vertical line to your plot using *`geom_vline()` 
*with the argument `xintercept`. To compute the true population standard *
*deviation you might refer directly to *`EUFstudents_fem[["Height"]]`*!*

```{r sampex-6-setup}
set.seed(123)
mcs_result <- purrr::map_dbl(
  .x = seq_len(1000), 
  .f = ~sd(sample(x = EUFstudents_fem[["Height"]], size = 20))
  )
mcs_result_tbl <- tibble::as_tibble(mcs_result)
```

```{r sampex-6, exercise=TRUE, warning=FALSE, message=FALSE}
mcs_result_tbl
```

```{r sampex-6-hint-1}
ggplot(data = ____, mapping = ____) +
  ____ +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-2}
ggplot(data = mcs_result_tbl, mapping = ____) +
  ____ +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-3}
ggplot(data = mcs_result_tbl, mapping = aes(x=____)) +
  ____ +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-4}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  ____ +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-5}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  geom_____ +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-6}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  geom_histogram() +
  ____ +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-7}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  geom_histogram() +
  geom_vline(xintercept = ____) +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-hint-8}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  geom_histogram() +
  geom_vline(xintercept = sd(____)) +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-solution}
ggplot(data = mcs_result_tbl, mapping = aes(x=value)) +
  geom_histogram() +
  geom_vline(xintercept = sd(EUFstudents_fem[["Height"]])) +
  scale_y_continuous(expand = expansion()) +
  theme_bw()
```

```{r sampex-6-check}
grader <- grade_this({
  fail_if(!ggcheck::is_ggplot(.result), 
          message = paste0(
            "You did not define a `ggplot` object. Use the function ",
            "`ggplot2::ggplot()`. ",
            "Did you maybe forget to call and render the plot?"
            )
          )
  fail_if(!ggcheck::uses_data(.result, mcs_result_tbl), 
          message = paste0(
            "You should use the data set `mcs_result_tbl`. You can pass ",
            "it to the argument `data` of `ggplot2::ggplot()`."
            )
          )
  fail_if(!uses_mappings(.result, aes(x = value), exact = TRUE), 
          message = paste0(
            "Since you are asked to create a histogram, you should map the " ,
            "variable `value` to the x-axis! Use the argument `mapping` ",
            "of the `ggplot2::ggplot()` function, together with `ggplot2::aes()`."
            )
          )  
  fail_if(!ggcheck::uses_geoms(.result, c("histogram"), exact = FALSE), 
          message = paste0(
            "You were asked to construct a histogram... ",
            "What geom would you use to do this?"
            )
          )
  fail_if(!ggcheck::uses_geoms(.result, c("vline"), exact = FALSE), 
          message = paste0(
            "You were asked to add a vertical line representing the standard ",
            "deviation of the population. Use `geom_vline()` to achieve this!"
            )
          )
  bare_code <- str_remove_all(as.character(.user_code), " ")
  spec_eval <- (str_detect(bare_code, "sd\\(") & 
                  str_detect(bare_code, "Height") & 
                  str_detect(bare_code, "EUFstudents_fem"))
  if (!spec_eval){
    fail(paste0(
      "To compute the standard deviation of the true population you ",
      "must apply the function 'sd()' to the values of the correct column of ",
      "`EUFstudents_fem`!"))
    }
  # Does not yet work:
  # x_intercept <- sd(EUFstudents_fem[["Height"]])
  # if(!uses_geom_params(.result, "vline", list(xintercept = x_intercept))){
  #   fail(paste0(
  #     "You forgot the set the argument `xintercept` for the vline ",
  #     "geom to the standard deviation of the population. To compute the true ",
  #     "standard deviation do something like `sd(EUFstudents_fem[['Height']])`!"))
  # }
  pass()
})
```
