---
title: "Project organization and data import"
author: "Introduction to data science: session 6"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(data.table)
library(tibble)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE, 
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
```

## Project organization - content quiz

```{r quiz}
quiz(
  question(
    "How can you display your current working directory?",
    answer("Via the function `getwd()`.", correct = TRUE),
    answer("Via the function `cwd()`."),
    answer(paste0(
      "By clicking on ",
      "`Session/Set Working Directory/Print Working Directory` in R-Studio.")),
    answer("By searching for the `.Rproj` file in your file explorer."),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Which of the following statements about working directories are correct?",
    answer("The working directory cannot be changed once fixed within an R-project"),
    answer(paste0("If you use relative paths, they usually start ", 
                  "from your current working directory"), 
           correct=TRUE),
    answer("The default working directory for R is the user directory", 
           correct = TRUE),
    answer(paste0("If you open an R-project, the working directory is set to ", 
                  "the location of the `.Rproj`-file.")),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question("What is the difference between absolute and relative paths?",
    answer(paste0("Absolute paths start at the root, ", 
                  "relative paths at the working directory"), 
           correct=TRUE),
    answer(paste0("Absolute paths are unambiguous across projects, relative ",
                  "paths not necessarily")),
    answer(paste0("Absolute paths contain a file name, relative paths ",
                  "only point to the directory in which files might be stored")),
    answer(paste0("Relative paths are always relative to the `.Rproj`-file ",
                  "of the current project, absolute paths always start at ",
                  "the working directory.")),
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Should you generally use absolute or relative paths?",
    answer(paste0("You should avoid absolute paths since they are " ,
                  "usually computer-specific"), correct=TRUE),
    answer(paste0(
      "For the sake of transparency, absolute paths are preferable ",
      "since they contain the whole paths, starting from the computer root.")),
    answer(paste0("Relative paths are always a bad idea because ", 
                  "they are dependent on your current working directory.")),
    answer(paste0("It does not really matter, both have their pros and cons.")),
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    paste0("When creating a new project directory, which of the ",
           "following sub-directories should you create per default?"),
    answer("`R`, which contains all R scripts", correct=TRUE),
    answer("`output`, in which you save all output produced by your scripts", 
           correct=TRUE),
    answer("`text`, in which you save all written text", correct=TRUE),
    answer("`misc`, in which you store everything that doesn't fit elsewhere", 
           correct=TRUE),
    answer("`bin`, which serves as the garbage bin for this project"),
    answer("`plots`, in which you save your visualizations"),
    answer("`input`, in which you save your raw data that serves as input"),
    answer(paste0(
      "`public`, in which you store files meant for all public users ", 
      "(such as `LICENSE.md` or `README.md`).")),
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What is the package `here` used for?",
    answer(paste0(
      "It takes relative paths as an argument, and produces ",
      "computer-specific absolute paths, based on information about the ",
      "relative location of the current file in your R project"), 
      correct=TRUE),
    answer(paste0(
      "It automatically sets the working directory of your ",
      "project to the place of the nearest `.Rproj` file, ",
      "allowing you to run code on different computers")),
    answer(paste0(
      "After setting your position via `here::i_am()` you can ",
      "translate arbitrary file paths into paths to your current ",
      "working directory.")),
    answer(paste0(
      "It provides a number of functions that allow you to change the ",
      "working directory, to create new R-projects, and to facilitate code ",
      "sharing.")),
    allow_retry = TRUE, random_answer_order = TRUE
  )
)
```

## Project organization - coding exercises

For the following exercises, assume that your project has the following 
directory structure and you are working from within the script `myscript.R`:

```
Exercise6
│   Exercise6.Rproj    
│
└───data
│   │
│   └───tidy
│       │   mydata.csv
│   └───raw
└───R
    │   myscript.R
```

**What should the first two lines in the file `myscript.R` look like if you will**
**use the package `here` in this script?**

```{r ex-proj1, exercise=TRUE, message=TRUE, warning=FALSE, echo=FALSE, error=TRUE}

```

```{r ex-proj1-hint-1}
____
library(____)
```

```{r ex-proj1-hint-2}
____
library(here)
```

```{r ex-proj1-hint-3}
here::____
library(here)
```

```{r ex-proj1-hint-4}
here::i_am(____)
library(here)
```

```{r ex-proj1-hint-5}
here::i_am("R/____")
library(here)
```

```{r ex-proj1-solution}
here::i_am("R/myscript.R")
library(here)
```

```{r ex-proj1-check}
grade_this({
    fail_if(!stringr::str_detect(.user_code, "'R/myscript.R'"), 
          message = paste0(
            "Remember to tell `R` about the relative position of `myscript.R`. ",
            "Use the `i_am()` function form the package `here`!"
            )
          )
    fail_if_code_feedback(
          message = paste0(
            "Remember to tell `R` about the relative position of `myscript.R`" ,
            "in the beginning. Use the `i_am()` function form the package ",
            "`here`! Only after this you should attach the `here` package as ",
            "such."
            )
          )
  pass()
})
```

Create an absolute path using the `here` package to the file `mydata.csv`.
Assume that `here` is already attached, but make
sure you use the `::`-notation to be explicit.

```{r ex-proj2, exercise=TRUE, message=TRUE, warning=FALSE, echo=FALSE, error=TRUE}

```

```{r ex-proj2-solution}
here::here("data/tidy/mydata.csv")
```

```{r ex-proj2-hint-1}
here::here(____)
```

```{r ex-proj2-hint-2}
here::here("____")
```

```{r ex-proj2-hint-3}
here::here("data/____/____")
```

```{r ex-proj2-hint-4}
here::here("data/____/mydata.csv")
```

```{r ex-proj2-check}
grade_this({
fail_if(!stringr::str_detect(.user_code, "here\\("), 
          message = paste0(
            "Your code is missing the call of the function `here()` with a ",
            "character vector representing the relative path to `mydata.csv`!"
            )
          )
  
      fail_if(!stringr::str_detect(.user_code, "data/tidy/mydata.csv"), 
          message = paste0(
            "Your code does not contain the correct relative path to ",
            "`mydata.csv`, which is located in the subdirectory `data/table/`."
            )
          )
      pass_if(identical(.result, here::here('data/tidy/mydata.csv')))
  fail()
})
```

## Data import - content quiz

```{r quiz2}
quiz(
  question(
    "Which function from which package should you use to import `csv`-files?",
    answer("`data.table::fread()`", correct = TRUE),
    answer("`data.table::fwrite()`"),
    answer("`dplyr::fread()`"),
    answer("`readr::read_csv()`"),
    answer("`tidyverse::fread()`"),
    answer("`read.csv()`")
  ),
  question(
    "Which function should you use to save `csv`-files?",
    answer("`data.table::fread()`"),
    answer("`data.table::fwrite()`", correct = TRUE),
    answer("`saveRDS()`"),
    answer("`save()`"),
    answer("`tidyverse::fwrite()`"),
    answer("`data.table::write_csv()`")
  ),
  question(
    "What is the difference between `.Rds`-files and `.Rdata`-files?",
    answer(paste("`.Rds`-files contain single R objects,",
                 "`.Rdata`-files may contain several"), 
           correct = TRUE),
    answer(paste("`.Rdata`-files contain single R objects,",
                 "`.Rds`-files may contain several")),
    answer(paste("`.Rdata`-files can be loaded without additional packages,",
                 "`.Rds`-files require the package `tidyerse`.")),
    answer(paste("`.Rdata`-files are faster to read and write, but the",
                 "compression level of `.Rds`-files is much better."))
  ),
  question(paste0(
    "To read `.Rds`-files you use `readRDS()`, to read `Rda`-files you use `load()`.",
    "In what sense do these functions differ in terms of their behavior?"),
    answer("`readRDS()` returns an object, `load()` does not return anything.", 
           correct = TRUE),
    answer("`load` returns an object, `readRDS()` does not return anything."),
    answer("Both behave the same way."),
    answer(paste("`load` returns object of type `data.frame`,",
                 "the objects of `readRDS()` retain their original type."))
  ),
  question(paste0(
    "What is the default type of the objects returned by `data.table::fread()`?"),
    answer("`data.table`", correct = TRUE),
    answer("`data.frame`"),
    answer("`tibble`"),
    answer("`table`"),
    answer("Depends on the input file.")
  )
  )
```


## Data import - coding exercises

For the following exercises, assume that your project has the following 
directory structure with all data sets being located directly within the
folder `data`, and you are working from within the script `myscript.R`:

```
Exercise6
│   Exercise6.Rproj    
│
└───data
│   │   growth_data_1.csv
|   |   product_complexity.csv
|   |   unemp_pop.csv
└───R
    │   myscript.R
```

**Attention:** Due to the way these exercises were created you cannot use
the function `here()`, as you would usually do. Thus, use relative paths from
the project main directory, i.e. the paths you would normally pass to the 
function `here()`.

https://rstudio.github.io/learnr/articles/exercises.html

Mit Datensätzen, die du in dem Slides Projekt erstellt hast

**Import the file `growth_data_1.csv`, assign to the resulting object the, **
**name `growth_data`, transform it into a `tibble`, and call the object by** 
**its name. The file looks like this:**

```
country;Growth;year
Germany;-4.56961671737398;2020
Germany;1.05550824713283;2019
Germany;1.08602451412267;2018
Germany;2.68023111405891;2017
Germany;2.22999986782015;2016
Germany;1.49193152760772;2015
```

**Make sure you set the decimal sign and the column separator explicitly!**

```{r ex-imp1, exercise=TRUE}

```

```{r ex-imp1-hint-1}
growth_data <- ____(
  ____ = ____, 
  ____ = ____, 
  ____ = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-2}
growth_data <- data.table::____(
  ____ = ____, 
  ____ = ____, 
  ____ = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-3}
growth_data <- data.table::fread(
  ____ = ____, 
  ____ = ____, 
  ____ = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-4}
growth_data <- data.table::fread(
  ____ = "data/growth_data_1.csv", 
  ____ = ____, 
  ____ = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-5}
growth_data <- data.table::fread(
  ____ = "data/growth_data_1.csv", 
  sep = ____, 
  ____ = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-6}
growth_data <- data.table::fread(
  ____ = "data/growth_data_1.csv", 
  sep = ____, 
  dec = ____)
growth_data <- ____(growth_data)
growth_data
```

```{r ex-imp1-hint-7}
growth_data <- data.table::fread(
  ____ = "data/growth_data_1.csv", 
  sep = ____, 
  dec = ____)
growth_data <- tibble::____(growth_data)
growth_data
```

```{r ex-imp1-hint-8}
growth_data <- data.table::fread(
  ____ = "data/growth_data_1.csv", 
  sep = ____, 
  dec = ____)
growth_data <- tibble::as_tibble(growth_data)
growth_data
```

```{r ex-imp1-hint-9}
growth_data <- data.table::fread(
  file = "data/growth_data_1.csv", 
  sep = ____, 
  dec = ____)
growth_data <- tibble::as_tibble(growth_data)
growth_data
```

```{r ex-imp1-hint-10}
growth_data <- data.table::fread(
  file = "data/growth_data_1.csv", 
  sep = ____, 
  dec = ____)
growth_data <- tibble::as_tibble(growth_data)
growth_data
```

```{r ex-imp1-hint-11}
growth_data <- data.table::fread(
  file = "data/growth_data_1.csv", 
  sep = ";", 
  dec = ____)
growth_data <- tibble::as_tibble(growth_data)
growth_data
```

```{r ex-imp1-solution}
growth_data <- data.table::fread(
  file = "data/growth_data_1.csv", 
  sep = ";", 
  dec = ".")
growth_data <- tibble::as_tibble(growth_data)
growth_data
```

```{r ex-imp1-check}
growth_data <- tibble::as_tibble(data.table::fread(
  file = "data/growth_data_1.csv", 
  sep = ";", 
  dec = "."))

grade_this({
  fail_if(stringr::str_detect(.user_code, "here\\("), 
            message = paste0(
              "Your code should not use the function `here::here()`, although ",
              "you should usually use this function. But for the sake of this ",
              "exercise simply use the relative paths you would usually have ",
              "passed to `here::here()`."
              )
          )
  fail_if(!tibble::is_tibble(.result), 
            message = paste0(
              "Your solution is not a tibble. Did you forget to return it? Or ",
              "did you forget to transform the imported data into a `tibble`? ",
              "The package `tibble` contains a function with which you can ",
              "transform data frames into a `tibble`!"
              )
          )
  print(.user_code)
  fail_if(!stringr::str_detect(.user_code, "fread"), 
            message = paste0(
              "You need to use the function `fread()` from the package ",
              "`data.table` to import the data!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "sep"), 
            message = paste0(
              "You forgot to set the column separator explicitly. Check out ",
              "the possible arguments to `data.table::fread()`!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "dec"), 
            message = paste0(
              "You forgot to set the decimal sign explicitly. Check out ",
              "the possible arguments to `data.table::fread()`!"
              )
          )
  pass_if(identical(.result, growth_data))
  fail()
})
```


**Import the file `product_complexity.csv`. Assign to the resulting object the **
**name `product_complexity`, transform it into a `tibble`, and call the object by** 
**its name. The file looks like this:**

```
commoditycode.product_complexity.exp_share
0101.0,0642426217529412.4,64
0102.-0,492542902941177.3,7
0103.0,510823855941177.4,082
0104.-1,12472420411765.0,916
0105.-0,173124057611765.1,331
0106.-1,37125134705882.0,766
0201.-0,103990797158824.25,346
0202.-0,989652876470588.5,429
0203.0,858757858235294.23,61
0204.-0,891279994705882.5,466
```

**Do not forget to set the decimal sign and the column separator explicitly!**

```{r ex-imp2, exercise=TRUE}

```

```{r ex-imp2-solution}
product_complexity <- data.table::fread(
  file = "data/product_complexity.csv",
  sep = ".", dec = ",",
  colClasses = c("character", rep("double", 2))
  )
product_complexity <- tibble::as_tibble(product_complexity)
product_complexity
```

```{r ex-imp2-check}
product_complexity <- tibble::as_tibble(data.table::fread(
  file = "data/product_complexity.csv",
  sep = ".", dec = ",",
  colClasses = c("character", rep("double", 2))
  ))

grade_this({
  fail_if(stringr::str_detect(.user_code, "here\\("), 
            message = paste0(
              "Your code should not use the function `here::here()`, although ",
              "you should usually use this function. But for the sake of this ",
              "exercise simply use the relative paths you would usually have ",
              "passed to `here::here()`."
              )
          )
  fail_if(!tibble::is_tibble(.result), 
            message = paste0(
              "Your solution is not a tibble. Did you forget to return it? Or ",
              "did you forget to transform the imported data into a `tibble`? ",
              "The package `tibble` contains a function with which you can ",
              "transform data frames into a `tibble`!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "fread"), 
            message = paste0(
              "You need to use the function `fread()` from the package ",
              "`data.table` to import the data!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "sep"), 
            message = paste0(
              "You forgot to set the column separator explicitly. Check out ",
              "the possible arguments to `data.table::fread()`!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "dec"), 
            message = paste0(
              "You forgot to set the decimal sign explicitly. Check out ",
              "the possible arguments to `data.table::fread()`!"
              )
          )
  fail_if(!is.character(.result[["commoditycode"]]), 
            message = paste0(
              "The column `commoditycode` should be of type `character`, ",
              "otherwise the columns are not read correctly. In your solution ",
              "its of type {typeof(.result[['commoditycode']])}. You should ",
              "set the column types via the correct argument in `fread()`!"
              )
          )
  fail_if(!is.double(.result[["product_complexity"]]), 
            message = paste0(
              "The column `product_complexity` should be of type `double`, ",
              "otherwise the columns are not read correctly. In your solution ",
              "its of type {typeof(.result[['product_complexity']])}. You should ",
              "set the column types via the correct argument in `fread()`!"
              )
          )
  fail_if(!is.double(.result[["exp_share"]]), 
            message = paste0(
              "The column `exp_share` should be of type `double`, ",
              "otherwise the columns are not read correctly. In your solution ",
              "its of type {typeof(.result[['exp_share']])}. You should ",
              "set the column types via the correct argument in `fread()`!"
              )
          )
  pass_if(identical(.result, product_complexity))
  fail()
})
```

**Import the file `unemp_pop.csv`, but only the columns `country`, `year`, **
**and `labor_force`, and only the first two rows. Also, make sure that the **
**data set is saved as a `tibble`, and that the variable `labor_force` has **
**the type `double`, and the variable `year` has the type `integer`.**

```
country,year,population,labor_force
Germany,2015,81686611,42654597
Germany,2016,82348669,43551192
Germany,2017,82657002,43789062
Germany,2018,82905782,43884544
Germany,2019,83092962,44351163
Germany,2020,83240525,44120268
```

```{r ex-imp3, exercise=TRUE}

```

```{r ex-imp3-hint-1}
unemp_pop <- ____(
  ____ = ____,
  ____ = ____, 
  ____ = ____,
  ____ = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-2}
unemp_pop <- data.table::fread(
  ____ = ____,
  ____ = ____, 
  ____ = ____,
  ____ = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-3}
unemp_pop <- data.table::fread(
  file = ____,
  ____ = ____, 
  ____ = ____,
  ____ = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-4}
unemp_pop <- data.table::fread(
  file = ____,
  sep = ____, 
  ____ = ____,
  ____ = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-5}
unemp_pop <- data.table::fread(
  file = ____,
  sep = ____, 
  select = ____,
  ____ = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-6}
unemp_pop <- data.table::fread(
  file = ____,
  sep = ____, 
  select = ____,
  nrows = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-7}
unemp_pop <- data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ____, 
  select = ____,
  nrows = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-8}
unemp_pop <- data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ",", 
  select = c(____=____, ____=____, ____=____),
  nrows = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-9}
unemp_pop <- data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ",", 
  select = c("country"="character", ____=____, ____=____),
  nrows = ____)
unemp_pop <- ____(unemp_pop)
unemp_pop
```

```{r ex-imp3-hint-10}
unemp_pop <- data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ",", 
  select = c("country"="character", ____=____, ____=____),
  nrows = 2)
unemp_pop <- tibble::as_tibble(unemp_pop)
unemp_pop
```

```{r ex-imp3-solution}
unemp_pop <- data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ",", 
  select = c("country"="character", "year"="integer", "labor_force"="double"),
  nrows = 2)
unemp_pop <- tibble::as_tibble(unemp_pop)
unemp_pop
```

```{r ex-imp3-check}
unemp_pop <- tibble::as_tibble(data.table::fread(
  file = "data/unemp_pop.csv",
  sep = ",", 
  select = c("country"="character", "year"="integer", "labor_force"="double"),
  nrows = 2)
  )

grade_this({
  fail_if(stringr::str_detect(.user_code, "here\\("), 
            message = paste0(
              "Your code should not use the function `here::here()`, although ",
              "you should usually use this function. But for the sake of this ",
              "exercise simply use the relative paths you would usually have ",
              "passed to `here::here()`."
              )
          )
  fail_if(!tibble::is_tibble(.result), 
            message = paste0(
              "Your solution is not a tibble. Did you forget to return it? Or ",
              "did you forget to transform the imported data into a `tibble`? ",
              "The package `tibble` contains a function with which you can ",
              "transform data frames into a `tibble`!"
              )
          )
  fail_if(!stringr::str_detect(.user_code, "fread"), 
            message = paste0(
              "You need to use the function `fread()` from the package ",
              "`data.table` to import the data!"
              )
          )
  fail_if(!is.double(.result[["labor_force"]]), 
            message = paste0(
              "The column `labor_force` should be of type `double`. ",
              "In your solution, however, ",
              "its of type {typeof(.result[['labor_force']])}. You should ",
              "set the column types via the correct argument in `fread()`!"
              )
          )
  fail_if(!is.integer(.result[["year"]]), 
            message = paste0(
              "The column `year` should be of type `integer`. ",
              "In your solution, however, ",
              "its of type {typeof(.result[['year']])}. You should ",
              "set the column types via the correct argument in `fread()`!"
              )
          )
  fail_if(!setequal(names(.result), names(unemp_pop)), 
          message = paste0(
            "You should only keep the columns `country`, `year`, and ",
            "`labor_force`, but the tibble you created contains the columns ",
            "{paste(names(.result), collapse=', ')}. There are different ",
            "possibilities. Check out the help function for `fread()` or read ",
            "the tutorial on data import."
            )
          )
  fail_if(nrow(.result)!=2, 
          message = paste0(
            "You should only keep the first two rows of the data. ",
            "Check out the help function for `fread()` or read ",
            "the tutorial on data import to find out how to do it. Or search ",
            "the web;)"
            )
          )
  pass_if(identical(.result, unemp_pop))
  fail()
})
```
