---
title: "Basics in R: Functions"
author: "Claudius Gräbner-Radkowitsch"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup(
  pass.praise = TRUE, fail.hint = FALSE,
  fail.encourage = TRUE, maybe_code_feedback = FALSE)
tutorial_options(exercise.blanks = "____")
```

# Functions

## Content quiz

```{r functionquiz}
quiz(
  question(
    "Which of the following statements about functions in R is/are correct?",
    answer("Functions apply a certain routine on an input, thereby producing (almost always) an output.", correct=TRUE),
    answer("Are the R equivalent to mathematical functions and map numbers from one mathematical space into another."),
    answer("Functions facilitate the debugging of your code, especially if they encapsulate routines that use multiple times.", correct=TRUE),
    answer("Functions are difficult to define for yourself, so you should mainly use pre-defined functions and avoid user-written functions whenever possible."),
    answer("As a rule of thumb, whenever you use some code more than twice, you should encapsulate it into a function.", correct=TRUE), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "What do we need optional arguments for?",
    answer("They represent the input to a function and are, thus, necessary for the function to produce an output."),
    answer("They usually help us to adjust the routine implemented in the function to the particular case at hand.", correct=TRUE),
    answer("These kind of arguments are unnecessary. Since they are optional its safe to ignore them until you become a more experienced programmer."),
    answer("All arguments to functions are optional in the strict sense, so there is nothing special about them."), 
    allow_retry = TRUE, random_answer_order = TRUE
  ),
  question(
    "Consider the function `sum()`. What is its main argument?",
    answer("An arbitrary number of numeric or logical atomic vectors", correct=TRUE),
    answer("A single vector containing numerical elements that the function can sum up."),
    answer("A logical vector named `na.rm`, indicating whether the function should ignore missing values when suming up a vector."),
    answer("The name of the vector of which you want to sum up the elements."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Consider the function `sum()`. What is its optional argument?",
    answer("A logical vector named `na.rm`, indicating whether the function should ignore missing values when suming up a vector.", correct=TRUE),
    answer("The name of the vector of which you want to sum up the elements."),
    answer("A single vector containing numerical elements that the function can sum up."),
    answer("The function `sum()` has no optional arguments."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Only optional arguments can be specified by name. Is this true?",
    answer("No, you can also specify mandatory arguments by name, but this is not necessary.", correct=TRUE),
    answer("Yes, mandatory arguments have no name and must be entered in the sequence they are mentioned in the function definition."),
    answer("No, in fact only mandatory arguments can be specified by name, optional arguments are specified by position."),
    answer("Yes, the name of mandatory arguments is only used for documentation purposes."), 
    allow_retry = TRUE, random_answer_order = TRUE
    ),
  question(
    "Variables that are defined within the function body...",
    answer("disappear after the function has been called.", correct=TRUE),
    answer("remain available after calling the function and can be used to check intermediate results."),
    answer("disappear by default, but can be kept if the universal optional argument `keep_int_vars` is set to `TRUE`."), 
    allow_retry = TRUE, random_answer_order = TRUE)
)
```

## Coding exercises I: defining basic functions

### Simple addition

Define a function called `man_add` that formalizes the equation $f(x,y)=x+y$, 
Thus, the function takes two mandatory
arguments and adds them up. 

Test your function for the values $x=2$ and $y=4$.

```{r ex-defadd, exercise=TRUE, exercise.lines=8}

```

```{r ex-defadd-hint-1}
man_add <- function(x, y){
  # function body
}
man_add(____)
```

```{r ex-defadd-hint-2}
man_add <- function(x, y){
  result <- ____ + ____
  return(result)
}
man_add(____)
```

```{r ex-defadd-hint-3}
man_add <- function(x, y){
  result <- ____ + ____
  return(result)
}
man_add(x = 2, y = 4)
```

```{r ex-defadd-hint-4}
man_add <- function(x, y){
  result <- x + ____
  return(result)
}
man_add(x = 2, y = 4)
```

```{r ex-defadd-solution}
man_add <- function(x, y){
  result <- x + y
  return(result)
}
man_add(x = 2, y = 4)
```

```{r ex-defadd-check}
grader <- grade_this({
  print(.user_code)
  if ( !stringr::str_detect(.user_code, "function\\(")){
    fail(message = paste0(
      "You need to use the function `function()` to define a new function.")
      )
  }

  if ( !stringr::str_detect(.user_code, "man_add\\(")){
    fail(message = paste0(
      "You should define and use a function called 'man_add'.")
      )
  }
  
  if ( !is.double(.result)){
    fail(message = paste0(
      "Your solution is not a number, did you forget to call your function or ",
      "to make sure it returns its result?")
    )
  }
  
  if (identical(.result, 2+4)){
    pass()
  }

  fail()
})
```

### A funny function

Write a function `funny` that takes as an input two numbers, $x$ and $y$, and
then return $\left(x+y\right)^2$ times the string "Ha". For example, for
$x=2$ and $y=2$, the function should return `"HaHaHaHa"`. 

> Hint: To turn a vector `c("Ha", "Ha")` into `"Haha"`, you can do: 
`paste(c("Ha", "Ha"), collapse = "")`

Test your function for $x=4$ and $y=5$!

```{r ex-funny, exercise=TRUE, exercise.lines=8}

```

```{r ex-funny-hint-1}
funny <- function(x, y){
  # function body
}
funny(____)
```

```{r ex-funny-hint-2}
funny <- function(x, y){
  nb_of_has <- ____
  ha_string <- ____
  result <- ____
  return(result)
}
funny(____)
```

```{r ex-funny-hint-3}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- ____
  result <- ____
  return(result)
}
funny(____)
```

```{r ex-funny-hint-4}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep(____,____)
  result <- ____
  return(result)
}
funny(____)
```

```{r ex-funny-hint-5}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep("Ha",nb_of_has)
  result <- ____
  return(result)
}
funny(____)
```

```{r ex-funny-hint-6}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep("Ha",nb_of_has)
  result <- paste(____, collapse = "")
  return(result)
}
funny(____)
```

```{r ex-funny-hint-7}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep("Ha",nb_of_has)
  result <- paste(ha_string, collapse = "")
  return(result)
}
funny(____)
```

```{r ex-funny-hint-8}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep("Ha",nb_of_has)
  result <- paste(ha_string, collapse = "")
  return(result)
}
funny(x = ____, y = ____)
```

```{r ex-funny-solution}
funny <- function(x, y){
  nb_of_has <- (x+y)**2
  ha_string <- rep("Ha", nb_of_has)
  result <- paste(ha_string, collapse = "")
  return(result)
}
funny(x = 4, y = 5)
```

```{r ex-funny-check}

correct_solution <- paste(rep("Ha", 81), collapse = "")

grader <- grade_this({
  print(.user_code)
  if ( !stringr::str_detect(.user_code, "function\\(")){
    fail(message = paste0(
      "You need to use the function `function()` to define a new function.")
      )
  }

  if ( !stringr::str_detect(.user_code, "funny\\(")){
    fail(message = paste0(
      "You should define and use a function called 'funny'.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "paste")){
    fail(message = paste0(
      "You must use the function `paste` as suggested in the hint.")
      )
  }
  
  if (!is.character(.result)){
    fail(message = paste0(
      "Your solution is not a character vector, did you forget to call your ",
      "function or to make sure it returns its result?")
    )
  }
  
  if (identical(.result, correct_solution)){
    pass()
  }

  fail()
})
```


### Law of gravity
Newton's law of gravitation describes the force of gravity between two objects, 
$F$, in terms of a universal constant, $G$, the masses of the two objects, 
$m_1$ and $m_2$, and the distance between the objects, $r$.

The law of gravitation is given by the following equation:

$$F=G\frac{m_1\cdot m_2}{r} $$

Write a function `gravity`, which computes this equation. Note that $G$ is
already pre-defined (you can check it by calling `G` in the console). So your
function requires only three arguments.

Test your function for the case of $m_1=2$, $m_2=5$ and $r=0.5$.

```{r ex-gravity-setup}
G <- 6.673*(10**(-11))
```

```{r ex-gravity, exercise=TRUE, exercise.lines=8}

```

```{r ex-gravity-hint-1}
gravity <- function(____, ____, ____){
  # Function body
}
gravity(____)
```

```{r ex-gravity-hint-2}
gravity <- function(m1, ____, ____){
  # Function body
}
gravity(____)
```

```{r ex-gravity-hint-3}
gravity <- function(m1, m2, r){
  # Function body
}
gravity(____)
```

```{r ex-gravity-hint-4}
gravity <- function(m1, m2, r){
  result <- ____
  return(result)
}
gravity(____)
```

```{r ex-gravity-hint-5}
gravity <- function(m1, m2, r){
  result <- G*____*____/____
  return(result)
}
gravity(____)
```

```{r ex-gravity-hint-6}
gravity <- function(m1, m2, r){
  result <- G*m1*____/____
  return(result)
}
gravity(____)
```

```{r ex-gravity-hint-7}
gravity <- function(m1, m2, r){
  result <- G*m1*m2/____
  return(result)
}
gravity(____)
```

```{r ex-gravity-hint-8}
gravity <- function(m1, m2, r){
  result <- G*m1*m2/r
  return(result)
}
gravity(____)
```

```{r ex-gravity-hint-9}
gravity <- function(m1, m2, r){
  result <- G*m1*m2/r
  return(result)
}
gravity(m1 = ____, m2 = ____, r = ____)
```

```{r ex-gravity-hint-10}
gravity <- function(m1, m2, r){
  result <- G*m1*m2/r
  return(result)
}
gravity(m1 = 2, m2 = ____, r = ____)
```


```{r ex-gravity-solution}
gravity <- function(m1, m2, r){
  result <- G*m1*m2/r
  return(result)
}
gravity(m1 = 2, m2 = 5, r = 0.5)
```


```{r ex-gravity-check}
gravity_solution <- function(m1, m2, r){
  result <- G*m1*m2/r
  return(result)
}
correct_solution <- gravity_solution(m1 = 2, m2 = 5, r = 0.5)

grader <- grade_this({
  print(.user_code)
  if ( !stringr::str_detect(.user_code, "function\\(")){
    fail(message = paste0(
      "You need to use the function `function()` to define a new function.")
      )
  }

  if ( !stringr::str_detect(.user_code, "gravity\\(")){
    fail(message = paste0(
      "You should define and use a function called 'gravity'.")
      )
  }
  
  if ( !stringr::str_detect(.user_code, "G")){
    fail(message = paste0(
      "The equation includes the gravitational constant G, which has been ",
      "pre-defined. You need to use it in your solution!")
      )
  }
  
  if ( !is.double(.result)){
    fail(message = paste0(
      "Your solution is not a number, did you forget to call your function or ",
      "to make sure it returns its result?")
    )
  }
  
  if (identical(.result, correct_solution)){
    pass()
  }

  fail()
})
```


## Coding exercises II: defining more complicated functions

Define a function called `my_var_func` that takes a vector of numbers as an input
and calculates the sample variance. Note that the formula for the variance is:

$$\frac{\sum_i(x_i-\bar{x})^2}{n-1}$$

where $\bar{x}$ is the mean of $x$, and $n$ the number of elements in x.
Note also that $\bar{x}$ can be computed as `mean(x)` and a sum can be 
computed using `sum()`.

Test your function by applying it to the pre-defined input `test_vector`.

```{r ex-deffun-setup}
test_vector <- seq(1, 8, by=0.25)
```

```{r ex-deffun, exercise=TRUE, exercise.lines=8}

```

```{r ex-deffun-hint-1}
my_var_func <- function(x){
  # function body
}
```

```{r ex-deffun-hint-2}
my_var_func <- function(x){
  x_mean <- mean(x)
  # ...
}
```

```{r ex-deffun-hint-3}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  # ...
}
```

```{r ex-deffun-hint-4}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  # ...
}
```

```{r ex-deffun-solution}
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  x_var <- sum(squared_dev) / (x_len-1)
  return(x_var)
}
```

```{r ex-deffun-check}
grade_result(
  pass_if(~identical(.result, var(test_vector)))
)
```

Take the function you defined above and document it according to the rules
that you have read about in the tutorial.

```{r ex-docfun, exercise=TRUE, exercise.lines=8}

```

```{r ex-docfun-hint-1}
# Each documentation should contain a short title, a short description, the
# function arguments and the return value.
```

```{r ex-docfun-hint-2}
# The documentation of a function must come immediately before the function
# definition and each line of the documentation starts with `#'`. 
# In the first line you provide a title, which must not be longer than 80 
# characetrs.

# Then, after inserting a blank line you describe what the function does in a bit 
# more detail. Then, you describe each argument by using the decorator `@param` 
# at the beginning of the lines. Finally, after another blank line, you describe 
# the output of the function after starting the line with the decorator `@return`.
```

```{r ex-docfun-solution}
#' Computes the variance of a vector
#' 
#' This function takes a numeric vector as input and computes the sample
#'  variance. It does not work if missing values are presend.
#' @param x An atomic vector of type `double` or `integer`
#' @return The sample variance of `x` as `double`
my_var_func <- function(x){
  x_mean <- mean(x)
  x_len <- length(x)
  squared_dev <- (x - x_mean)**2
  x_var <- sum(squared_dev) / (x_len-1)
  return(x_var)
}
```
